---
title: "arrival timing histogram"
author: "MNSnyder"
date: "2/1/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---


Grande Ronde summer steelhead Columbia River temperature time series from 2017. 
4 scenarios included:

* Columbia River 2017
* Columbia River 2017, no CWRs
* Columbia River 2017 plus 1
* Columbia River 2017 plus 1, no CWRs

Snake River fall Chinook Columbia River temperature time series from 2017. 
4 scenarios included:

* Columbia River 2017
* Columbia River 2017, no CWRs
* Columbia River 2017 plus 1
* Columbia River 2017 plus 1, no CWRs

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE)
library(ggplot2)
library(cowplot)
library(data.table)
library(knitr)
library(chron)
library(readr)
library(lubridate)
```

```{r set up directories, echo=FALSE}
# to run script on different computers specify sys.info()[4] and
# specify path to model results folder and
# folder containing look up tables

# Marcia's epa computer -> NOT SET UP
if(Sys.info()[4]=="LZ2626XMSNYDE02"){
  fishdir<-path.expand("D:/Results_Columbia/Columbia_Migration_chnk2/Columbia_Migration_chnk2-[1]/") # results path
  scenario<-"Columbia_Migration_chnk2" # scenario name
  inputdir<-path.expand("D:/HexSim_Models/CWR_Columbia/Columbia [small]/Analysis/Data Lookup/") # path to look up tables
  caldir<-path.expand("D:/HexSim_Models/CWR_Columbia/R_code/") # calibration data directory
}

# Marcia's Lenovo -> SET UP
if(Sys.info()[4]=="DESKTOP-KMUP1V2"){
  fishdir<-path.expand("C:/Users/snyde/Dropbox/")
  outputdir<-path.expand("C:/Users/snyde/Dropbox/")
  }
```

```{r import end condition}
# import in combined replicate DFs
A13<-read.table(paste(fishdir,"Results_4Populations/gr_Columbia2017B/combined/E13.csv", sep=""), header=TRUE, sep=",")
B13<-read.table(paste(fishdir,"Results_4Populations/gr_Columbia2017B_NoCWR/combined/F13.csv", sep=""), header=TRUE, sep=",")
C13<-read.table(paste(fishdir,"Results_4Populations/gr_Columbia2017BplusOne/combined/G13.csv",  sep=""),header=TRUE, sep=",")
D13<-read.table(paste(fishdir,"Results_4Populations/gr_Columbia2017BplusOne_NoCWR/combined/H13.csv", sep=""), header=TRUE, sep=",")

# rename DF columns
names(A13)<-c("Run", "Step", "Population", "ID", "Time_entry", "Time_exit", "Time_in_system", "Time_remaining", "Total_hours_cold_water", "Initial_weight", "Initial_energy_density", "Fitness_weight", "Fitness_energy_density", "Fitness_energy")
names(B13)<-c("Run", "Step", "Population", "ID", "Time_entry", "Time_exit", "Time_in_system", "Time_remaining", "Total_hours_cold_water", "Initial_weight", "Initial_energy_density", "Fitness_weight", "Fitness_energy_density", "Fitness_energy")
names(C13)<-c("Run", "Step", "Population", "ID", "Time_entry", "Time_exit", "Time_in_system", "Time_remaining", "Total_hours_cold_water", "Initial_weight", "Initial_energy_density", "Fitness_weight", "Fitness_energy_density", "Fitness_energy")
names(D13)<-c("Run", "Step", "Population", "ID", "Time_entry", "Time_exit", "Time_in_system", "Time_remaining", "Total_hours_cold_water", "Initial_weight", "Initial_energy_density", "Fitness_weight", "Fitness_energy_density", "Fitness_energy")

```


```{r created energy used for all scenarios without gamete}
# function to calculate cumulative degree days above a certain degree
avail_energy_diff<-function(DF){
  DF$gamete<-(((7598 + (0.527 * DF$Initial_weight)) * DF$Initial_weight) * 0.068) / DF$Initial_weight
DF$initial_ED_avail<-DF$Initial_energy_density-DF$gamete
# create column of energy lost
# energy_all$energy_lost<-energy_all$X11 - energy_all$X13
DF$energy_lost_gamete<-(DF$initial_ED_avail - DF$Fitness_energy) 
DF$ED_per_used<-(DF$energy_lost_gamete/DF$initial_ED_avail) * 100
return(DF)
}

A13<-avail_energy_diff(A13)
B13<-avail_energy_diff(B13)
C13<-avail_energy_diff(C13)
D13<-avail_energy_diff(D13)

# add scenario identifying column
A13$scenario<-"A"
B13$scenario<-"B"
C13$scenario<-"C"
D13$scenario<-"D"

# combine DFs 
all_13<-rbind.data.frame(A13, B13, C13, D13)
```


```{r time in system histogram}
# all_13$Time_in_system_d<-all_13$Time_in_system / 24
# all_13_labels<-all_13
# # vector of scenario labels
# all_13_labels$scenario<-as.factor(all_13_labels$scenario)
# levels(all_13_labels$scenario)[levels(all_13_labels$scenario)=="A"] <-"Columbia 2017, CWR Current"
# levels(all_13_labels$scenario)[levels(all_13_labels$scenario)=="B"] <-"Columbia 2017, No CWR"
# levels(all_13_labels$scenario)[levels(all_13_labels$scenario)=="C"] <-"Columbia 2040 (2017), CWR Current"
# levels(all_13_labels$scenario)[levels(all_13_labels$scenario)=="D"] <-"Columbia 2040 (2017), No CWR"


#v_names<-c("Columbia 2040- CWR Current", "Columbia Restored- CWR Current","Columbia Current- CWR Current", "Columbia #Current- CWR Restored", "Columbia 2040- No CWRs", "Columbia Restored- No CWRs","Columbia Current- No CWRs" )
#p <- ggplot(data = all_13_labels, aes(x = Time_in_system_d, group = scenario)) + geom_histogram(binwidth = 5)
#p + facet_wrap(~scenario) + labs(x="Passage time (d)", y="Count", title="Grande Ronde River Summer Steelhead")

```


```{r terminus arrival histogram preparation}
# model starts on July 1 which is equivalent to julian day 182
jday_start<-182

all_13_labels<-all_13
# step is hour arrived at terminus
# convert Step to julian day
all_13_labels$terminus_jday<-floor(all_13_labels$Step / 24) + jday_start
# convert julian day to date
all_13_labels$terminus_date_ch<-chron(all_13_labels$terminus_jday, origin=c(month=1, day=1, year=2019))
# convert date format to posixct
all_13_labels$terminus_date<- as.POSIXct(all_13_labels$terminus_date_ch, "GMT") 

# Time_entry is hour started from Bonneville
# convert Step to julian day
all_13_labels$entry_jday<-floor(all_13_labels$Time_entry / 24) + jday_start
# convert julian day to date
all_13_labels$entry_date_ch<-chron(all_13_labels$entry_jday, origin=c(month=1, day=1, year=2019))
# convert date format to posixct
all_13_labels$entry_date<- as.POSIXct(all_13_labels$entry_date_ch, "GMT") 

# filter into two different datasets
sub1<-dplyr::filter(all_13_labels, scenario == "Columbia 2017, CWR Current" | scenario == "Columbia 2017, No CWR" )
sub2<-dplyr::filter(all_13_labels, scenario == "Columbia 2040 (2017), CWR Current" | scenario == "Columbia 2040 (2017), No CWR" )

```

```{r terminus arrival histogram}
# histograms
# 2017 temperature Columbia River
# p <- ggplot(data = sub1, aes(x = terminus_date,  fill=scenario)) + geom_histogram(position="dodge") + theme_classic()
# p +  labs(x="Exit Day", y="Count", fill="", title="Grande Ronde River Summer Steelhead") + 
#   scale_color_manual(values=c("#999999", "#E69F00", "#56B4E9")) + 
#   scale_fill_manual(values=c("#999999", "#E69F00", "#56B4E9"),labels=c("Columbia 2017", "Columbia 2017 / No CWR"))+
#   theme(axis.text=element_text(size=14),
#         axis.title=element_text(size=14),
#         legend.text = element_text(size=14), legend.position = c(.95, .95),
#   legend.justification = c("right", "top"))
# 
# # 2040 temperature Columbia River
# q <- ggplot(data = sub2, aes(x = terminus_date,  fill=scenario)) + geom_histogram(position="dodge") + theme_classic()
# q +  labs(x="Exit Day", y="Count", fill="", title="Grande Ronde River Summer Steelhead") + 
#   scale_color_manual(values=c("#999999", "#E69F00", "#56B4E9")) + 
#   scale_fill_manual(values=c("#999999", "#E69F00", "#56B4E9"),labels=c("Columbia 2040", "Columbia 2040 / No CWR"))+
#   theme(axis.text=element_text(size=14),
#         axis.title=element_text(size=14),
#         legend.text = element_text(size=14), legend.position = c(.95, .95),
#   legend.justification = c("right", "top"))

```

```{r}

all_13_labels$terminus_date2<-lubridate::as_date(all_13_labels$terminus_date)
min <- as.Date("07/01/19", format="%m/%d/%y")
max <- as.Date("10/30/19", format="%m/%d/%y")

p <- ggplot(data = all_13_labels, aes(x = terminus_date2, y = 100*(..count../sum(..count..)), group=scenario)) + geom_density( aes(linetype = scenario, color=scenario), size=1) + theme_classic()+
  ylim(0,0.35)+ scale_x_date(limits = c(min, max))+
  labs(x="Exit Day", y="Percentage", fill="", title="Grande Ronde River Summer Steelhead") +
  scale_linetype_manual(name="", values=c("solid", "twodash", "solid", "twodash"),labels = c("Current with CWRs", "Current without CWRs", "Future with CWRs", "Future without CWRs"))+
  scale_color_manual(name="", values=c('blue3','blue3', 'firebrick3','firebrick3'), labels = c("Current temperature with CWRs", "Current temperature without CWRs", "Future temperature with CWRs", "Future temperature without CWRs"))  +
  theme(axis.text=element_text(size=14),
        axis.title=element_text(size=14),
        legend.text = element_text(size=14), legend.position = "none",
  legend.justification = c("right", "top"), legend.title = element_blank())
p
```

```{r GR density}

# p <- ggplot(data = all_13_labels, aes(x = terminus_date, y = 100*(..count../sum(..count..)), group=scenario)) + geom_density( aes(linetype = scenario, color=scenario), size=1) + theme_classic()+
#     labs(x="Exit Day", y="Percentage", fill="", title="Grande Ronde River Summer Steelhead") +
#   scale_linetype_manual(name="", values=c("solid", "twodash", "solid", "twodash"),labels = c("Current with CWRs", "Current without CWRs", "Future with CWRs", "Future without CWRs"))+
#   scale_color_manual(name="", values=c('blue3','blue3', 'firebrick3','firebrick3'), labels = c("Current temperature with CWRs", "Current temperature without CWRs", "Future temperature with CWRs", "Future temperature without CWRs"))  +
#   theme(axis.text=element_text(size=14),
#         axis.title=element_text(size=14),
#         legend.text = element_text(size=14), legend.position = "none",
#   legend.justification = c("right", "top"), legend.title = element_blank())
# p
```


```{r terminus arrival density plot}
# histograms
# 2017 temperature Columbia River
# p <- ggplot(data = sub1, aes(x = terminus_date, fill=scenario)) + geom_density( alpha=0.5) + theme_classic()
# p +  labs(x="Exit Day", y="Count", fill="", title="Grande Ronde River Summer Steelhead") + 
#   scale_color_manual(values=c("darkorange3", "blue4")) + 
#   scale_fill_manual(values=c( "darkorange3", "blue4"),labels=c("Columbia 2017", "Columbia 2017 / No CWR")) +
#   theme(axis.text=element_text(size=14),
#         axis.title=element_text(size=14),
#         legend.text = element_text(size=14), legend.position = c(.95, .95),
#   legend.justification = c("right", "top"))
# 
# # 2040 temperature Columbia River
# p <- ggplot(data = sub2, aes(x = terminus_date, fill=scenario)) + geom_density( alpha=0.5) + theme_classic()
# p +  labs(x="Exit Day", y="Count", fill="", title="Grande Ronde River Summer Steelhead") + 
#   scale_color_manual(values=c("darkorange3", "blue4")) + 
#   scale_fill_manual(values=c( "darkorange3", "blue4"),labels=c("Columbia 2040", "Columbia 2040 / No CWR")) +
#   theme(axis.text=element_text(size=14),
#         axis.title=element_text(size=14),
#         legend.text = element_text(size=14), legend.position = c(.95, .95),
#   legend.justification = c("right", "top"))

```


####################################################################
###################################################################
# SNAKE RIVER


```{r import end condition}
# import in combined replicate DFs
A13sr<-read.table(paste(fishdir,"Results_4Populations/snake_Columbia2017B/combined/E4.csv", sep=""), header=TRUE, sep=",")
B13sr<-read.table(paste(fishdir,"Results_4Populations/snake_Columbia2017B_NoCWR/combined/F4.csv", sep=""), header=TRUE, sep=",")
C13sr<-read.table(paste(fishdir,"Results_4Populations/snake_Columbia2017BplusOne/combined/G4.csv",  sep=""),header=TRUE, sep=",")
D13sr<-read.table(paste(fishdir,"Results_4Populations/snake_Columbia2017BplusOne_NoCWR/combined/H4.csv",  sep=""),header=TRUE, sep=",")

# rename DF columns
names(A13sr)<-c("Run", "Step", "Population", "ID", "Time_entry", "Time_exit", "Time_in_system", "Time_remaining", "Total_hours_cold_water", "Initial_weight", "Initial_energy_density", "Fitness_weight", "Fitness_energy_density", "Fitness_energy")
names(B13sr)<-c("Run", "Step", "Population", "ID", "Time_entry", "Time_exit", "Time_in_system", "Time_remaining", "Total_hours_cold_water", "Initial_weight", "Initial_energy_density", "Fitness_weight", "Fitness_energy_density", "Fitness_energy")
names(C13sr)<-c("Run", "Step", "Population", "ID", "Time_entry", "Time_exit", "Time_in_system", "Time_remaining", "Total_hours_cold_water", "Initial_weight", "Initial_energy_density", "Fitness_weight", "Fitness_energy_density", "Fitness_energy")
names(D13sr)<-c("Run", "Step", "Population", "ID", "Time_entry", "Time_exit", "Time_in_system", "Time_remaining", "Total_hours_cold_water", "Initial_weight", "Initial_energy_density", "Fitness_weight", "Fitness_energy_density", "Fitness_energy")

```


```{r created energy used for all scenarios without gamete}
# function to calculate cumulative degree days above a certain degree
avail_energy_diff<-function(DF){
  DF$gamete<-(((7598 + (0.527 * DF$Initial_weight)) * DF$Initial_weight) * 0.068) / DF$Initial_weight
DF$initial_ED_avail<-DF$Initial_energy_density-DF$gamete
# create column of energy lost
# energy_all$energy_lost<-energy_all$X11 - energy_all$X13
DF$energy_lost_gamete<-(DF$initial_ED_avail - DF$Fitness_energy) 
DF$ED_per_used<-(DF$energy_lost_gamete/DF$initial_ED_avail) * 100
return(DF)
}

A13sr<-avail_energy_diff(A13sr)
B13sr<-avail_energy_diff(B13sr)
C13sr<-avail_energy_diff(C13sr)
D13sr<-avail_energy_diff(D13sr)

# add scenario identifying column
A13sr$scenario<-"A"
B13sr$scenario<-"B"
C13sr$scenario<-"C"
D13sr$scenario<-"D"

# combine DFs 
all_13sr<-rbind.data.frame(A13sr, B13sr, C13sr, D13sr)
```

```{r time in system histogram}
all_13sr$Time_in_system_d<-all_13sr$Time_in_system / 24
all_13_labelssr<-all_13sr
# vector of scenario labels
all_13_labelssr$scenario<-as.factor(all_13_labelssr$scenario)
levels(all_13_labelssr$scenario)[levels(all_13_labelssr$scenario)=="A"] <-"Columbia 2017, CWR Current"
levels(all_13_labelssr$scenario)[levels(all_13_labelssr$scenario)=="B"] <-"Columbia 2017, No CWR"
levels(all_13_labelssr$scenario)[levels(all_13_labelssr$scenario)=="C"] <-"Columbia 2040 (2017), CWR Current"
levels(all_13_labelssr$scenario)[levels(all_13_labelssr$scenario)=="D"] <-"Columbia 2040 (2017), No CWR"


# p <- ggplot(data = all_13_labelssr, aes(x = Time_in_system_d)) + geom_histogram(binwidth = 5)
# p + facet_wrap(~scenario) + labs(x="Passage time (d)", y="Count", title="Snake River fall Chinook")

```

```{r terminus arrival histogram preparation}
# rename
sr<-all_13_labelssr
# model starts on July 1 which is equivalent to julian day 182
jday_start<-182

# step is hour arrived at terminus
# convert Step to julian day
sr$terminus_jday<-floor(sr$Step / 24) + jday_start
# convert julian day to date
sr$terminus_date_ch<-chron(sr$terminus_jday, origin=c(month=1, day=1, year=2019))
# convert date format to posixct
sr$terminus_date<- as.POSIXct(sr$terminus_date_ch, "GMT") 

# Time_entry is hour started from Bonneville
# convert Step to julian day
sr$entry_jday<-floor(sr$Time_entry / 24) + jday_start
# convert julian day to date
sr$entry_date_ch<-chron(sr$entry_jday, origin=c(month=1, day=1, year=2019))
# convert date format to posixct
sr$entry_date<- as.POSIXct(sr$entry_date_ch, "GMT") 

# filter into two different datasets
sub1<-dplyr::filter(sr, scenario == "Columbia 2017, CWR Current" | scenario == "Columbia 2017, No CWR" )
sub2<-dplyr::filter(sr, scenario == "Columbia 2040 (2017), CWR Current" | scenario == "Columbia 2040 (2017), No CWR" )
```

```{r}
sr$terminus_date2<-lubridate::as_date(sr$terminus_date)
min <- as.Date("07/01/19", format="%m/%d/%y")
max <- as.Date("10/30/19", format="%m/%d/%y")
z <- ggplot(data = sr, aes(x = terminus_date2, y = 100*(..count../sum(..count..)), group=scenario)) + geom_density(stat='density', aes(linetype = scenario, color=scenario), size=1) + theme_classic()+
  labs(x="Exit Day", y="Percentage", fill="", title="Snake River Fall Chinook Salmon") +
  ylim(0,0.35)+ scale_x_date(limits = c(min, max))+
  scale_linetype_manual(name="", values=c("solid", "twodash", "solid", "twodash"),labels = c("Current with CWRs", "Current without CWRs", "Future with CWRs", "Future without CWRs"))+
  scale_color_manual(name="", values=c('blue3','blue3', 'firebrick3','firebrick3'), labels = c("Current temperature with CWRs", "Current temperature without CWRs", "Future temperature with CWRs", "Future temperature without CWRs"))  +
  theme(axis.text=element_text(size=14),
        axis.title=element_text(size=14),
        legend.text = element_text(size=14), legend.position = "none",
  legend.justification = c("right", "top"), legend.title = element_blank())

z
```

```{r density percent test}
# z <- ggplot(data = sr, aes(x = terminus_date, y = 100*(..count../sum(..count..)), group=scenario)) + geom_density(stat='density', aes(linetype = scenario, color=scenario), size=1) + theme_classic()+
#   labs(x="Exit Day", y="Percentage", fill="", title="Snake River Fall Chinook Salmon") +
#   scale_linetype_manual(name="", values=c("solid", "twodash", "solid", "twodash"),labels = c("Current with CWRs", "Current without CWRs", "Future with CWRs", "Future without CWRs"))+
#   scale_color_manual(name="", values=c('blue3','blue3', 'firebrick3','firebrick3'), labels = c("Current temperature with CWRs", "Current temperature without CWRs", "Future temperature with CWRs", "Future temperature without CWRs"))  +
#   theme(axis.text=element_text(size=14),
#         axis.title=element_text(size=14),
#         legend.text = element_text(size=14), legend.position = "none",
#   legend.justification = c("right", "top"), legend.title = element_blank())
# 
# z
```


```{r SR density}
# z <- ggplot(data = sr, aes(x = terminus_date, group=scenario)) + geom_density( aes(linetype = scenario, color=scenario), size=1) + theme_classic()+
#   labs(x="Exit Day", y="Count", fill="", title="Snake River Fall Chinook Salmon") +
#   scale_linetype_manual(name="", values=c("solid", "twodash", "solid", "twodash"),labels = c("Current with CWRs", "Current without CWRs", "Future with CWRs", "Future without CWRs"))+
#   scale_color_manual(name="", values=c('blue3','blue3', 'firebrick3','firebrick3'), labels = c("Current temperature with CWRs", "Current temperature without CWRs", "Future temperature with CWRs", "Future temperature without CWRs"))  +
#   theme(axis.text=element_text(size=14),
#         axis.title=element_text(size=14),
#         legend.text = element_text(size=14), legend.position = "none",
#   legend.justification = c("right", "top"), legend.title = element_blank())
# 
# z
```

```{r export plots}
res1 = 300
width1 = 4.0
height1 = 3.0
png(paste(outputdir,"Manuscript CWR Columbia/draft figures/arrival timing/SR_hist_arrival.png", sep=""),res=res1, width=width1, height=height1, units="in", type="windows", antialias = "none")
par(mar=c(6, 4, 4, 2) + 0.5)
 z
dev.off() 

png(paste(outputdir,"Manuscript CWR Columbia/draft figures/arrival timing/GR_hist_arrival.png", sep=""),res=res1, width=width1, height=height1, units="in", type="windows", antialias = "none")
par(mar=c(6, 4, 4, 2) + 0.1)
 p
dev.off() 
```



