---
title: "GR_energy_loss_table"
author: "MNSnyder"
date: "12/11/2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

Imports end condition data probe for Grande Ronde summer steelhead modeled fish for four scenarios:

* Columbia River 2017 - A
* Columbia River 2017, no CWRs - B
* Columbia River 2017 plus 1 - C
* Columbia River 2017 plus 1, no CWRs - D

1. calculates % energy lost per individual
2. calculates quantiles of energy lost
3. calculates number of fish using CWR and not using CWR for fish using less than 25% of energy (25 percentile of energy loss for scenario A)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(StreamThermal)
library(ggplot2)
library(cowplot)
library(data.table)
library(knitr)
library(chron)
library(lubridate)
library(dplyr)

```

```{r import end condition data, eval=TRUE}
# import in combined replicate DFs
A_end<-read.table("D:/Results_4Populations/gr_Columbia2017B/combined/E13.csv", header=TRUE, sep=",")
B_end<-read.table("D:/Results_4Populations/gr_Columbia2017B_NoCWR/combined/F13.csv", header=TRUE, sep=",")
C_end<-read.table("D:/Results_4Populations/gr_Columbia2017BplusOne/combined/G13.csv", header=TRUE, sep=",")
D_end<-read.table("D:/Results_4Populations/gr_Columbia2017BplusOne_NoCWR/combined/H13.csv", header=TRUE, sep=",")

# rename DF columns
names(A_end)<-c("Run", "Step", "Population", "ID", "Time_entry", "Time_exit", "Time_in_system", "Time_remaining", "Total_hours_cold_water", "Initial_weight", "Initial_energy_density", "Fitness_weight", "Fitness_energy_density", "Fitness_energy")
names(B_end)<-c("Run", "Step", "Population", "ID", "Time_entry", "Time_exit", "Time_in_system", "Time_remaining", "Total_hours_cold_water", "Initial_weight", "Initial_energy_density", "Fitness_weight", "Fitness_energy_density", "Fitness_energy")
names(C_end)<-c("Run", "Step", "Population", "ID", "Time_entry", "Time_exit", "Time_in_system", "Time_remaining", "Total_hours_cold_water", "Initial_weight", "Initial_energy_density", "Fitness_weight", "Fitness_energy_density", "Fitness_energy")
names(D_end)<-c("Run", "Step", "Population", "ID", "Time_entry", "Time_exit", "Time_in_system", "Time_remaining", "Total_hours_cold_water", "Initial_weight", "Initial_energy_density", "Fitness_weight", "Fitness_energy_density", "Fitness_energy")

```


```{r calculate percent energy lost}
# function to calculate cumulative degree days above a certain degree
avail_energy_diff<-function(DF){
  DF$gamete<-(((7598 + (0.527 * DF$Initial_weight)) * DF$Initial_weight) * 0.068) / DF$Initial_weight
DF$initial_ED_avail<-DF$Initial_energy_density-DF$gamete
# create column of energy lost
# energy_all$energy_lost<-energy_all$X11 - energy_all$X13
DF$energy_lost_gamete<-(DF$initial_ED_avail - DF$Fitness_energy) 
DF$ED_per_used<-(DF$energy_lost_gamete/DF$initial_ED_avail) * 100
return(DF)
}

# apply function to get % energy loss
A_energy<-avail_energy_diff(A_end)
B_energy<-avail_energy_diff(B_end)
C_energy<-avail_energy_diff(C_end)
D_energy<-avail_energy_diff(D_end)

quantile(A_energy$ED_per_used, c(0.50, 0.6, 0.7, 0.8, 0.9))
quantile(B_energy$ED_per_used, c(0.50, 0.6, 0.7, 0.8, 0.9))
quantile(C_energy$ED_per_used, c(0.50, 0.6, 0.7, 0.8, 0.9))
quantile(D_energy$ED_per_used, c(0.50, 0.6, 0.7, 0.8, 0.9))


count_cwr_fish<- function(DF){
DF$refuge_use<-ifelse(DF$Total_hours_cold_water > 4, 1, 0)
DF$refuge_use<-as.factor(DF$refuge_use)

DF %>% 
  group_by(refuge_use) %>%
filter(ED_per_used < 25) %>%
  count()

}

A_stats<-count_cwr_fish(A_energy)
B_stats<-count_cwr_fish(B_energy)
C_stats<-count_cwr_fish(C_energy)
D_stats<-count_cwr_fish(D_energy)

A_stats
B_stats
C_stats
D_stats

```

In scenario A, 52% of the individuals using < 25% of their energy use CWR, in scenario C, or under future Columbia River temperature, 42% of individuals use CWRs. 


