---
title: "Grande Ronde and Snake DD CDF plots"
author: "MNSnyder"
date: "11/19/2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

Creates reverse CDF for DD at 20,21, and 22 thresholds for Grande Ronde River Summer steelhead and Snake River Fall Chinook populations from HexSim output for 4 scenarios. 

Columbia River temperature time series from 2017. 
4 scenarios included:

* Columbia River 2017
* Columbia River 2017, no CWRs
* Columbia River 2017 plus 1
* Columbia River 2017 plus 1, no CWRs

Columbia 2017B assigns the John Day Pool temperature from the John Day forebay, which is the warmer part of the pool.


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE)
library(ggplot2)
library(cowplot)
library(data.table)
library(knitr)
library(chron)
library(egg)
```


```{r plot formatting}
width1 = 4.5
height1 = 3.5
text1 = 8

My_Theme_CDF = theme(
  axis.title.x = element_text(size = 16),
  axis.text.x = element_text(size = 16),
  axis.title.y = element_text(size = 16),   
  axis.text.y = element_text(size = 16),
  plot.margin = margin(6, 0, 6, 0)
)
```


```{r import hourly gr summer steelhead}
# import in combined replicate DFs
A14<-fread("D:/Results_4Populations/gr_Columbia2017B/combined/E14.csv", header=TRUE, sep=",")
B14<-fread("D:/Results_4Populations/gr_Columbia2017B_NoCWR/combined/F14.csv", header=TRUE, sep=",")
C14<-fread("D:/Results_4Populations/gr_Columbia2017BplusOne/combined/G14.csv", header=TRUE, sep=",")
D14<-fread("D:/Results_4Populations/gr_Columbia2017BplusOne_NoCWR/combined/H14.csv", header=TRUE, sep=",")

# rename columns
names(A14)<-c("Run", "Step", "Population", "ID", "entry_time", "exit_time", "time_in_system", "time_at_terminus", "river_km", "motivation", "temp_1", "temp_mean", "energy_density", "weight", "energy", "selector", "avoidance", "hours_cold_water_episodic", "hours_cold_water_total", "refuge_id", "hydropower")
names(B14)<-c("Run", "Step", "Population", "ID", "entry_time", "exit_time", "time_in_system", "time_at_terminus", "river_km", "motivation", "temp_1", "temp_mean", "energy_density", "weight", "energy", "selector", "avoidance", "hours_cold_water_episodic", "hours_cold_water_total", "refuge_id", "hydropower")
names(C14)<-c("Run", "Step", "Population", "ID", "entry_time", "exit_time", "time_in_system", "time_at_terminus", "river_km", "motivation", "temp_1", "temp_mean", "energy_density", "weight", "energy", "selector", "avoidance", "hours_cold_water_episodic", "hours_cold_water_total", "refuge_id", "hydropower")
names(D14)<-c("Run", "Step", "Population", "ID", "entry_time", "exit_time", "time_in_system", "time_at_terminus", "river_km", "motivation", "temp_1", "temp_mean", "energy_density", "weight", "energy", "selector", "avoidance", "hours_cold_water_episodic", "hours_cold_water_total", "refuge_id", "hydropower")

```


```{r dd calculate function}
# old function to calculate cumulative degree days above a certain degree
# dum_dd<-function(threshold, DF){
#   DF_subset<-DF[which(DF$temp_1 >= threshold),]
#   dd_threshold<-aggregate(temp_1~ID, data=DF_subset, sum)
#   dd_threshold$temp_1<-dd_threshold$temp_1/24
#   return(dd_threshold)
# }

# new function to calculate cumulative degree hours above a certain degree
dum_dd<-function(threshold, DF){
  DF_subset<-DF[which(DF$temp_1 >= threshold),]
  dd_threshold<-aggregate(temp_1~ID, data=DF_subset, sum)
  dd_threshold$temp_1<-dd_threshold$temp_1 / 24
  return(dd_threshold)
}

```


```{r function to calculate reverse CDF}
# function to get reverse of eCDF
rcdf <- function (x) {
     cdf <- ecdf(x)
     y <- cdf(x)
    xrcdf <- 1-y
}
```

###################################################################
## GR Degree Days > 20°C

```{r calc DD GT 20 for each scenario}

# set threshold
thres<-20
# run for each scenario's hourly DF
A14_ddGT18<-dum_dd(thres, A14)
B14_ddGT18<-dum_dd(thres, B14)
C14_ddGT18<-dum_dd(thres, C14)
D14_ddGT18<-dum_dd(thres, D14)

# add scenario column
A14_ddGT18$scenario<-"A"
B14_ddGT18$scenario<-"B"
C14_ddGT18$scenario<-"C"
D14_ddGT18$scenario<-"D"

#combine
all_14_ddGT18<-rbind.data.frame(A14_ddGT18, B14_ddGT18, C14_ddGT18, D14_ddGT18)

```


```{r GR reverse CDF 20}
#ggplot(all_14_ddGT18, aes(temp_1, colour = scenario)) + stat_ecdf()

a<-dplyr::filter(all_14_ddGT18, scenario=="A")
b<-dplyr::filter(all_14_ddGT18, scenario=="B")
c<-dplyr::filter(all_14_ddGT18, scenario=="C")
d<-dplyr::filter(all_14_ddGT18, scenario=="D")

# reverse ecdf for A
atest2<-rcdf(a$temp_1)
atest3<-cbind(atest2, a)
names(atest3)[1]<-'Percent'
# reverse ecdf for B
btest2<-rcdf(b$temp_1)
btest3<-cbind(btest2, b)
names(btest3)[1]<-'Percent'
# reverse ecdf for C
ctest2<-rcdf(c$temp_1)
ctest3<-cbind(ctest2, c)
names(ctest3)[1]<-'Percent'
# reverse ecdf for D
dtest2<-rcdf(d$temp_1)
dtest3<-cbind(dtest2, d)
names(dtest3)[1]<-'Percent'

rev_cdf_all<-rbind.data.frame(atest3, btest3, ctest3, dtest3)

gr_20<-ggplot(rev_cdf_all, aes(x =temp_1, y=Percent, group=scenario )) + 
  geom_line(aes(linetype=scenario, color=scenario), size=1) +
  theme_classic()+
  labs(x="Cumulative Degree Days (>20°C)", y="Proportion")+ xlim(0,1000)+
    scale_linetype_manual(name="", values=c("solid", "twodash", "solid", "twodash"), labels = c("Current temperature with CWRs", "Current temperature without CWRs", "Future temperature with CWRs", "Future temperature without CWRs"))+
  scale_color_manual(name="", values=c('blue3','blue3', 'firebrick3','firebrick3'), labels = c("Current temperature with CWRs", "Current temperature without CWRs", "Future temperature with CWRs", "Future temperature without CWRs")) + 
  My_Theme_CDF

```

###################################################################
## GR Degree Days > 21°C

```{r calc DD GT 21 for each scenario}

# set threshold
thres<-21
# run for each scenario's hourly DF
A14_ddGT18<-dum_dd(thres, A14)
B14_ddGT18<-dum_dd(thres, B14)
C14_ddGT18<-dum_dd(thres, C14)
D14_ddGT18<-dum_dd(thres, D14)

# add scenario column
A14_ddGT18$scenario<-"A"
B14_ddGT18$scenario<-"B"
C14_ddGT18$scenario<-"C"
D14_ddGT18$scenario<-"D"

#combine
all_14_ddGT18<-rbind.data.frame(A14_ddGT18, B14_ddGT18, C14_ddGT18, D14_ddGT18)

```

```{r reverse CDF 21}
#ggplot(all_14_ddGT18, aes(temp_1, colour = scenario)) + stat_ecdf()

a<-dplyr::filter(all_14_ddGT18, scenario=="A")
b<-dplyr::filter(all_14_ddGT18, scenario=="B")
c<-dplyr::filter(all_14_ddGT18, scenario=="C")
d<-dplyr::filter(all_14_ddGT18, scenario=="D")

# reverse ecdf for A
atest2<-rcdf(a$temp_1)
atest3<-cbind(atest2, a)
names(atest3)[1]<-'Percent'
# reverse ecdf for B
btest2<-rcdf(b$temp_1)
btest3<-cbind(btest2, b)
names(btest3)[1]<-'Percent'
# reverse ecdf for C
ctest2<-rcdf(c$temp_1)
ctest3<-cbind(ctest2, c)
names(ctest3)[1]<-'Percent'
# reverse ecdf for D
dtest2<-rcdf(d$temp_1)
dtest3<-cbind(dtest2, d)
names(dtest3)[1]<-'Percent'

rev_cdf_all<-rbind.data.frame(atest3, btest3, ctest3, dtest3)

gr_21<-ggplot(rev_cdf_all, aes(x =temp_1, y=Percent, group=scenario )) + 
  geom_line(aes(linetype=scenario, color=scenario), size=1) +
  theme_classic()+
  labs(x="Cumulative Degree Days (>21°C)", y="Proportion")+ xlim(0,1000)+
    scale_linetype_manual(name="", values=c("solid", "twodash", "solid", "twodash"), labels = c("Current temperature with CWRs", "Current temperature without CWRs", "Future temperature with CWRs", "Future temperature without CWRs"))+
  scale_color_manual(name="", values=c('blue3','blue3', 'firebrick3','firebrick3'), labels = c("Current temperature with CWRs", "Current temperature without CWRs", "Future temperature with CWRs", "Future temperature without CWRs"))+
  My_Theme_CDF

```

###################################################################
## GR Degree Days > 22°C

```{r calc DD GT 22 for each scenario}

# set threshold
thres<-22
# run for each scenario's hourly DF
A14_ddGT18<-dum_dd(thres, A14)
B14_ddGT18<-dum_dd(thres, B14)
C14_ddGT18<-dum_dd(thres, C14)
D14_ddGT18<-dum_dd(thres, D14)

# add scenario column
A14_ddGT18$scenario<-"A"
B14_ddGT18$scenario<-"B"
C14_ddGT18$scenario<-"C"
D14_ddGT18$scenario<-"D"

#combine
all_14_ddGT18<-rbind.data.frame(A14_ddGT18, B14_ddGT18, C14_ddGT18, D14_ddGT18)

```

```{r experiment with reverse CDF}
#ggplot(all_14_ddGT18, aes(temp_1, colour = scenario)) + stat_ecdf()

a<-dplyr::filter(all_14_ddGT18, scenario=="A")
b<-dplyr::filter(all_14_ddGT18, scenario=="B")
c<-dplyr::filter(all_14_ddGT18, scenario=="C")
d<-dplyr::filter(all_14_ddGT18, scenario=="D")


# reverse ecdf for A
atest2<-rcdf(a$temp_1)
atest3<-cbind(atest2, a)
names(atest3)[1]<-'Percent'
# reverse ecdf for B
btest2<-rcdf(b$temp_1)
btest3<-cbind(btest2, b)
names(btest3)[1]<-'Percent'
# reverse ecdf for C
ctest2<-rcdf(c$temp_1)
ctest3<-cbind(ctest2, c)
names(ctest3)[1]<-'Percent'
# reverse ecdf for D
dtest2<-rcdf(d$temp_1)
dtest3<-cbind(dtest2, d)
names(dtest3)[1]<-'Percent'

rev_cdf_all<-rbind.data.frame(atest3, btest3, ctest3, dtest3)

gr_22<-ggplot(rev_cdf_all, aes(x =temp_1, y=Percent, group=scenario )) + 
  geom_line(aes(linetype=scenario, color=scenario), size=1) +
  theme_classic()+
  labs(x="Cumulative Degree Days (>22°C)", y="Proportion")+ xlim(0,1000)+
    scale_linetype_manual(name="", values=c("solid", "twodash", "solid", "twodash"), labels = c("Current temperature with CWRs", "Current temperature without CWRs", "Future temperature with CWRs", "Future temperature without CWRs"))+
  scale_color_manual(name="", values=c('blue3','blue3', 'firebrick3','firebrick3'), labels = c("Current temperature with CWRs", "Current temperature without CWRs", "Future temperature with CWRs", "Future temperature without CWRs"))+  My_Theme_CDF

```



##################################################################
Snake River Fall Chinook-------------------------------------------
________________________________________________________________________

```{r import hourly sr fall chnk}
# import in combined replicate DFs
E14<-fread("D:/Results_4Populations/snake_Columbia2017B/combined/E5.csv", header=TRUE, sep=",")
F14<-fread("D:/Results_4Populations/snake_Columbia2017B_NoCWR/combined/F5.csv", header=TRUE, sep=",")
G14<-fread("D:/Results_4Populations/snake_Columbia2017BplusOne/combined/G5.csv", header=TRUE, sep=",")
H14<-fread("D:/Results_4Populations/snake_Columbia2017BplusOne_NoCWR/combined/H5.csv", header=TRUE, sep=",")

# rename columns
names(E14)<-c("Run", "Step", "Population", "ID", "entry_time", "exit_time", "time_in_system", "time_at_terminus", "river_km", "motivation", "temp_1", "temp_mean", "energy_density", "weight", "energy", "selector", "avoidance", "hours_cold_water_episodic", "hours_cold_water_total", "refuge_id", "hydropower")
names(F14)<-c("Run", "Step", "Population", "ID", "entry_time", "exit_time", "time_in_system", "time_at_terminus", "river_km", "motivation", "temp_1", "temp_mean", "energy_density", "weight", "energy", "selector", "avoidance", "hours_cold_water_episodic", "hours_cold_water_total", "refuge_id", "hydropower")
names(G14)<-c("Run", "Step", "Population", "ID", "entry_time", "exit_time", "time_in_system", "time_at_terminus", "river_km", "motivation", "temp_1", "temp_mean", "energy_density", "weight", "energy", "selector", "avoidance", "hours_cold_water_episodic", "hours_cold_water_total", "refuge_id", "hydropower")
names(H14)<-c("Run", "Step", "Population", "ID", "entry_time", "exit_time", "time_in_system", "time_at_terminus", "river_km", "motivation", "temp_1", "temp_mean", "energy_density", "weight", "energy", "selector", "avoidance", "hours_cold_water_episodic", "hours_cold_water_total", "refuge_id", "hydropower")

```

###################################################################
## SR Degree Days > 20°C

```{r SR calc DD GT 20 for each scenario}

# set threshold
thres<-20
# run for each scenario's hourly DF
E14_ddGT18<-dum_dd(thres, E14)
F14_ddGT18<-dum_dd(thres, F14)
G14_ddGT18<-dum_dd(thres, G14)
H14_ddGT18<-dum_dd(thres, H14)

# add scenario column
E14_ddGT18$scenario<-"A"
F14_ddGT18$scenario<-"B"
G14_ddGT18$scenario<-"C"
H14_ddGT18$scenario<-"D"

#combine
sr_ddGT20<-rbind.data.frame(E14_ddGT18, F14_ddGT18, G14_ddGT18, H14_ddGT18)

```


```{r SR reverse CDF 20}
#ggplot(all_14_ddGT18, aes(temp_1, colour = scenario)) + stat_ecdf()

a<-dplyr::filter(sr_ddGT20, scenario=="A")
b<-dplyr::filter(sr_ddGT20, scenario=="B")
c<-dplyr::filter(sr_ddGT20, scenario=="C")
d<-dplyr::filter(sr_ddGT20, scenario=="D")

# reverse ecdf for A
atest2<-rcdf(a$temp_1)
atest3<-cbind(atest2, a)
names(atest3)[1]<-'Percent'
# reverse ecdf for B
btest2<-rcdf(b$temp_1)
btest3<-cbind(btest2, b)
names(btest3)[1]<-'Percent'
# reverse ecdf for C
ctest2<-rcdf(c$temp_1)
ctest3<-cbind(ctest2, c)
names(ctest3)[1]<-'Percent'
# reverse ecdf for D
dtest2<-rcdf(d$temp_1)
dtest3<-cbind(dtest2, d)
names(dtest3)[1]<-'Percent'

rev_cdf_all20<-rbind.data.frame(atest3, btest3, ctest3, dtest3)

sr_20<-ggplot(rev_cdf_all20, aes(x =temp_1, y=Percent, group=scenario )) + 
  geom_line(aes(linetype=scenario, color=scenario), size=1) +
  theme_classic()+
  labs(x="Cumulative Degree Days (>20°C)", y="Proportion")+ xlim(0,500)+
    scale_linetype_manual(name="", values=c("solid", "twodash", "solid", "twodash"), labels = c("Current temperature with CWRs", "Current temperature without CWRs", "Future temperature with CWRs", "Future temperature without CWRs"))+
  scale_color_manual(name="", values=c('blue3','blue3', 'firebrick3','firebrick3'), labels = c("Current temperature with CWRs", "Current temperature without CWRs", "Future temperature with CWRs", "Future temperature without CWRs")) + 
  My_Theme_CDF

```

###################################################################
## SR Degree Days > 21°C

```{r SR calc DD GT 21 for each scenario}

# set threshold
thres<-21
# run for each scenario's hourly DF
E14_ddGT18<-dum_dd(thres, E14)
F14_ddGT18<-dum_dd(thres, F14)
G14_ddGT18<-dum_dd(thres, G14)
H14_ddGT18<-dum_dd(thres, H14)

# add scenario column
E14_ddGT18$scenario<-"A"
F14_ddGT18$scenario<-"B"
G14_ddGT18$scenario<-"C"
H14_ddGT18$scenario<-"D"

#combine
sr_ddGT21<-rbind.data.frame(E14_ddGT18, F14_ddGT18, G14_ddGT18, H14_ddGT18)

```


```{r SR reverse CDF 21}
#ggplot(all_14_ddGT18, aes(temp_1, colour = scenario)) + stat_ecdf()

a<-dplyr::filter(sr_ddGT21, scenario=="A")
b<-dplyr::filter(sr_ddGT21, scenario=="B")
c<-dplyr::filter(sr_ddGT21, scenario=="C")
d<-dplyr::filter(sr_ddGT21, scenario=="D")

# reverse ecdf for A
atest2<-rcdf(a$temp_1)
atest3<-cbind(atest2, a)
names(atest3)[1]<-'Percent'
# reverse ecdf for B
btest2<-rcdf(b$temp_1)
btest3<-cbind(btest2, b)
names(btest3)[1]<-'Percent'
# reverse ecdf for C
ctest2<-rcdf(c$temp_1)
ctest3<-cbind(ctest2, c)
names(ctest3)[1]<-'Percent'
# reverse ecdf for D
dtest2<-rcdf(d$temp_1)
dtest3<-cbind(dtest2, d)
names(dtest3)[1]<-'Percent'

rev_cdf_all21<-rbind.data.frame(atest3, btest3, ctest3, dtest3)

sr_21<-ggplot(rev_cdf_all21, aes(x =temp_1, y=Percent, group=scenario )) + 
  geom_line(aes(linetype=scenario, color=scenario), size=1) +
  theme_classic()+
  labs(x="Cumulative Degree Days (>21°C)", y="Proportion")+ xlim(0,500)+
    scale_linetype_manual(name="", values=c("solid", "twodash", "solid", "twodash"), labels = c("Current temperature with CWRs", "Current temperature without CWRs", "Future temperature with CWRs", "Future temperature without CWRs"))+
  scale_color_manual(name="", values=c('blue3','blue3', 'firebrick3','firebrick3'), labels = c("Current temperature with CWRs", "Current temperature without CWRs", "Future temperature with CWRs", "Future temperature without CWRs")) + 
  My_Theme_CDF

```

###################################################################
## SR Degree Days > 22°C

```{r SR calc DD GT 22 for each scenario}

# set threshold
thres<-22
# run for each scenario's hourly DF
E14_ddGT18<-dum_dd(thres, E14)
F14_ddGT18<-dum_dd(thres, F14)
G14_ddGT18<-dum_dd(thres, G14)
H14_ddGT18<-dum_dd(thres, H14)

# add scenario column
E14_ddGT18$scenario<-"A"
F14_ddGT18$scenario<-"B"
G14_ddGT18$scenario<-"C"
H14_ddGT18$scenario<-"D"

#combine
sr_ddGT22<-rbind.data.frame(E14_ddGT18, F14_ddGT18, G14_ddGT18, H14_ddGT18)

```


```{r SR reverse CDF 22}
#ggplot(all_14_ddGT18, aes(temp_1, colour = scenario)) + stat_ecdf()

a<-dplyr::filter(sr_ddGT22, scenario=="A")
b<-dplyr::filter(sr_ddGT22, scenario=="B")
c<-dplyr::filter(sr_ddGT22, scenario=="C")
d<-dplyr::filter(sr_ddGT22, scenario=="D")

# reverse ecdf for A
atest2<-rcdf(a$temp_1)
atest3<-cbind(atest2, a)
names(atest3)[1]<-'Percent'
# reverse ecdf for B
btest2<-rcdf(b$temp_1)
btest3<-cbind(btest2, b)
names(btest3)[1]<-'Percent'
# reverse ecdf for C
ctest2<-rcdf(c$temp_1)
ctest3<-cbind(ctest2, c)
names(ctest3)[1]<-'Percent'
# reverse ecdf for D
dtest2<-rcdf(d$temp_1)
dtest3<-cbind(dtest2, d)
names(dtest3)[1]<-'Percent'

rev_cdf_all22<-rbind.data.frame(atest3, btest3, ctest3, dtest3)

sr_22<-ggplot(rev_cdf_all22, aes(x =temp_1, y=Percent, group=scenario )) + 
  geom_line(aes(linetype=scenario, color=scenario), size=1) +
  theme_classic()+
  labs(x="Cumulative Degree Days (>22°C)", y="Proportion")+ xlim(0,500)+
    scale_linetype_manual(name="", values=c("solid", "twodash", "solid", "twodash"), labels = c("Current temperature with CWRs", "Current temperature without CWRs", "Future temperature with CWRs", "Future temperature without CWRs"))+
  scale_color_manual(name="", values=c('blue3','blue3', 'firebrick3','firebrick3'), labels = c("Current temperature with CWRs", "Current temperature without CWRs", "Future temperature with CWRs", "Future temperature without CWRs")) + 
  My_Theme_CDF

```

```{r plot reverse CDF together, fig.cap="Fig. X. Percent of population at any cumulative degree threshold that has greater cumulative exposure thant than the threshold."}

pg1<- plot_grid(
  gr_20 + theme(legend.position="none"),
  gr_21+ theme(legend.position="none"),
  gr_22 + theme(legend.position="none"),
  labels = c("A", "B", "C"),
  nrow = 3
)

# extract a legend that is laid out horizontally
legend_b <- get_legend(
  gr_20 + guides(color = guide_legend(nrow = 1)) +
    theme(legend.position = "bottom")
)

# add the legend underneath the row we made earlier. Give it 10%
# of the height of one plot (via rel_heights).
plot_grid(pg1, legend_b, nrow = 2, rel_heights = c(1, .1))
#plot_grid(gr_20, gr_21, gr_22,
#          labels = c("A", "B", "C"),
#          ncol = 1, nrow = 3)
```

```{r plot reverse CDF together2, fig.cap="Fig. X. Percent of population at any cumulative degree threshold that has greater cumulative exposure thant than the threshold."}

g1<- plot_grid(
  sr_20 + theme(legend.position="none"),
  sr_21+ theme(legend.position="none"),
  sr_22 + theme(legend.position="none"),
  labels = c("A", "B", "C"),
  nrow = 3
)

# extract a legend that is laid out horizontally
legend_b2 <- get_legend(
  sr_20 + guides(color = guide_legend(nrow = 1)) +
    theme(legend.position = "bottom")
)

# add the legend underneath the row we made earlier. Give it 10%
# of the height of one plot (via rel_heights).
plot_grid(g1, legend_b2, nrow = 2, rel_heights = c(1, .1))
#plot_grid(gr_20, gr_21, gr_22,
#          labels = c("A", "B", "C"),
#          ncol = 1, nrow = 3)
```

```{r plot reverse CDF together3, fig.width=8, fig.height=9, fig.cap="Fig. X. Percent of population at any cumulative degree threshold that has greater cumulative exposure thant than the threshold."}

g3<- plot_grid(
  gr_20 + theme(legend.position="none"),
  sr_20 + theme(legend.position="none"),
  gr_21+ theme(legend.position="none"),
  sr_21+ theme(legend.position="none"),
  gr_22 + theme(legend.position="none"),
  sr_22 + theme(legend.position="none"),
  labels = c("A", "B", "C", "D","E","F"),
  nrow = 3
)

# extract a legend that is laid out horizontally
legend_b2 <- get_legend(
  sr_20 + guides(color = guide_legend(nrow = 1)) +
    theme(legend.position = "bottom")
)

width1 = 9
height1 = 7
res1 = 300

png("C:/Users/msnyde02/OneDrive - Environmental Protection Agency (EPA)/Profile/Desktop/Manuscript CWR Columbia/GR_SR_rCDF_test.png", res=res1, width=width1, height=height1, units="in", type="windows", antialias = "none")


# add the legend underneath the row we made earlier. Give it 10%
# of the height of one plot (via rel_heights).
plot_grid(g3, legend_b2, nrow = 2, rel_heights = c(1, .1))
#plot_grid(gr_20, gr_21, gr_22,
#          labels = c("A", "B", "C"),
#          ncol = 1, nrow = 3)

dev.off()
```


```{r export plots individually}
width1 = 7
height1 = 4.5

## GR
png("C:/Users/msnyde02/OneDrive - Environmental Protection Agency (EPA)/Profile/Desktop/Manuscript CWR Columbia/draft figures/rCDF/GR_rCDF_A.png", res=res1, width=width1, height=height1, units="in", type="windows", antialias = "none")
 gr_20 + theme(legend.position="none")
dev.off() 

png("C:/Users/msnyde02/OneDrive - Environmental Protection Agency (EPA)/Profile/Desktop/Manuscript CWR Columbia/draft figures/rCDF/GR_rCDF_B.png", res=res1, width=width1, height=height1, units="in", type="windows", antialias = "none")
 gr_21 + theme(legend.position="none")
dev.off() 

png("C:/Users/msnyde02/OneDrive - Environmental Protection Agency (EPA)/Profile/Desktop/Manuscript CWR Columbia/draft figures/rCDF/GR_rCDF_C.png", res=res1, width=width1, height=height1, units="in", type="windows", antialias = "none")
 gr_22 + theme(legend.position="none")
dev.off() 

# SR
png("C:/Users/msnyde02/OneDrive - Environmental Protection Agency (EPA)/Profile/Desktop/Manuscript CWR Columbia/draft figures/rCDF/SR_rCDF_A.png", res=res1, width=width1, height=height1, units="in", type="windows", antialias = "none")
 sr_20 + theme(legend.position="none")
dev.off() 

png("C:/Users/msnyde02/OneDrive - Environmental Protection Agency (EPA)/Profile/Desktop/Manuscript CWR Columbia/draft figures/rCDF/SR_rCDF_B.png", res=res1, width=width1, height=height1, units="in", type="windows", antialias = "none")
 sr_21 + theme(legend.position="none")
dev.off() 

png("C:/Users/msnyde02/OneDrive - Environmental Protection Agency (EPA)/Profile/Desktop/Manuscript CWR Columbia/draft figures/rCDF/SR_rCDF_C.png", res=res1, width=width1, height=height1, units="in", type="windows", antialias = "none")
 sr_22 + theme(legend.position="none")
dev.off() 
  
width1 = 10
height1 = 4.5
# plot for legend
png("C:/Users/msnyde02/OneDrive - Environmental Protection Agency (EPA)/Profile/Desktop/Manuscript CWR Columbia/draft figures/rCDF/SR_rCDF_tick.png", res=res1, width=width1, height=height1, units="in", type="windows", antialias = "none")
sr_20 + guides(color = guide_legend(nrow = 1)) +
    theme(legend.position = "bottom")
dev.off() 

```









