---
title: "energy lost with error GR and SR"
author: "MNSnyder"
date: "1/7/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(cowplot)
library(data.table)
library(knitr)
library(chron)
library(lubridate)
library(dplyr)
library(plotly)
library(GGally)
library(doBy) # statistical summary function
library(stringr)
```

Creates mean (+ error bars) % energy used plot for Grande Ronde summer steelhead and Snake River Fall chinook populations. 

Grande Ronde summer steelhead Columbia River temperature time series from 2017. 
4 scenarios included:

* Columbia River 2017
* Columbia River 2017, no CWRs
* Columbia River 2017 plus 1
* Columbia River 2017 plus 1, no CWRs

Columbia 2017A assigns the John Day Pool temperature from the John Day forebay, which is the warmer part of the pool.


```{r import end condition}
# import in combined replicate DFs
A13<-read.table("D:/Results_4Populations/gr_Columbia2017B/combined/E13.csv", header=TRUE, sep=",")
B13<-read.table("D:/Results_4Populations/gr_Columbia2017B_NoCWR/combined/F13.csv", header=TRUE, sep=",")
C13<-read.table("D:/Results_4Populations/gr_Columbia2017BplusOne/combined/G13.csv", header=TRUE, sep=",")
D13<-read.table("D:/Results_4Populations/gr_Columbia2017BplusOne_NoCWR/combined/H13.csv", header=TRUE, sep=",")

# rename DF columns
names(A13)<-c("Run", "Step", "Population", "ID", "Time_entry", "Time_exit", "Time_in_system", "Time_remaining", "Total_hours_cold_water", "Initial_weight", "Initial_energy_density", "Fitness_weight", "Fitness_energy_density", "Fitness_energy")
names(B13)<-c("Run", "Step", "Population", "ID", "Time_entry", "Time_exit", "Time_in_system", "Time_remaining", "Total_hours_cold_water", "Initial_weight", "Initial_energy_density", "Fitness_weight", "Fitness_energy_density", "Fitness_energy")
names(C13)<-c("Run", "Step", "Population", "ID", "Time_entry", "Time_exit", "Time_in_system", "Time_remaining", "Total_hours_cold_water", "Initial_weight", "Initial_energy_density", "Fitness_weight", "Fitness_energy_density", "Fitness_energy")
names(D13)<-c("Run", "Step", "Population", "ID", "Time_entry", "Time_exit", "Time_in_system", "Time_remaining", "Total_hours_cold_water", "Initial_weight", "Initial_energy_density", "Fitness_weight", "Fitness_energy_density", "Fitness_energy")

```


```{r created energy used for all scenarios without gamete}
# function to calculate cumulative degree days above a certain degree
avail_energy_diff<-function(DF){
  DF$gamete<-(((7598 + (0.527 * DF$Initial_weight)) * DF$Initial_weight) * 0.068) / DF$Initial_weight
DF$initial_ED_avail<-DF$Initial_energy_density-DF$gamete
# create column of energy lost
# energy_all$energy_lost<-energy_all$X11 - energy_all$X13
DF$energy_lost_gamete<-(DF$initial_ED_avail - DF$Fitness_energy) 
DF$ED_per_used<-(DF$energy_lost_gamete/DF$initial_ED_avail) * 100
return(DF)
}

A13<-avail_energy_diff(A13)
B13<-avail_energy_diff(B13)
C13<-avail_energy_diff(C13)
D13<-avail_energy_diff(D13)

# add scenario identifying column
A13$scenario<-"Current with CWRs"
B13$scenario<-"Current without CWRs"
C13$scenario<-"Future with CWRs"
D13$scenario<-"Future without CWRs"

# combine DFs 
all_GR<-rbind.data.frame(A13, B13, C13, D13)
```



```{r import end condition}
# import in combined replicate DFs
E13<-read.table("D:/Results_4Populations/snake_Columbia2017B/combined/E4.csv", header=TRUE, sep=",")
F13<-read.table("D:/Results_4Populations/snake_Columbia2017B_NoCWR/combined/F4.csv", header=TRUE, sep=",")
G13<-read.table("D:/Results_4Populations/snake_Columbia2017BplusOne/combined/G4.csv", header=TRUE, sep=",")
H13<-read.table("D:/Results_4Populations/snake_Columbia2017BplusOne_NoCWR/combined/H4.csv", header=TRUE, sep=",")

# rename DF columns
names(E13)<-c("Run", "Step", "Population", "ID", "Time_entry", "Time_exit", "Time_in_system", "Time_remaining", "Total_hours_cold_water", "Initial_weight", "Initial_energy_density", "Fitness_weight", "Fitness_energy_density", "Fitness_energy")
names(F13)<-c("Run", "Step", "Population", "ID", "Time_entry", "Time_exit", "Time_in_system", "Time_remaining", "Total_hours_cold_water", "Initial_weight", "Initial_energy_density", "Fitness_weight", "Fitness_energy_density", "Fitness_energy")
names(G13)<-c("Run", "Step", "Population", "ID", "Time_entry", "Time_exit", "Time_in_system", "Time_remaining", "Total_hours_cold_water", "Initial_weight", "Initial_energy_density", "Fitness_weight", "Fitness_energy_density", "Fitness_energy")
names(H13)<-c("Run", "Step", "Population", "ID", "Time_entry", "Time_exit", "Time_in_system", "Time_remaining", "Total_hours_cold_water", "Initial_weight", "Initial_energy_density", "Fitness_weight", "Fitness_energy_density", "Fitness_energy")

```


```{r created energy used for all scenarios without gamete}
# function to calculate cumulative degree days above a certain degree
avail_energy_diff<-function(DF){
  DF$gamete<-(((7598 + (0.527 * DF$Initial_weight)) * DF$Initial_weight) * 0.068) / DF$Initial_weight
DF$initial_ED_avail<-DF$Initial_energy_density-DF$gamete
# create column of energy lost
# energy_all$energy_lost<-energy_all$X11 - energy_all$X13
DF$energy_lost_gamete<-(DF$initial_ED_avail - DF$Fitness_energy) 
DF$ED_per_used<-(DF$energy_lost_gamete/DF$initial_ED_avail) * 100
return(DF)
}

E13<-avail_energy_diff(E13)
F13<-avail_energy_diff(F13)
G13<-avail_energy_diff(G13)
H13<-avail_energy_diff(H13)

# add scenario identifying column
E13$scenario<-"Current with CWRs"
F13$scenario<-"Current without CWRs"
G13$scenario<-"Future with CWRs"
H13$scenario<-"Future without CWRs"

# combine DFs 
all_snake<-rbind.data.frame(E13, F13, G13, H13)
```

```{r statistical summary function}
## Summarizes data.
## Gives count, mean, standard deviation, standard error of the mean, and confidence 
## interval (default 95%).
##   data: a data frame.
##   measurevar: the name of a column that contains the variable to be summariezed
##   groupvars: a vector containing names of columns that contain grouping variables
##   na.rm: a boolean that indicates whether to ignore NA's
##   conf.interval: the percent range of the confidence interval (default is 95%)
summarySE <- function(data=NULL, measurevar, groupvars=NULL, na.rm=FALSE, conf.interval=.95) {
    library(doBy)

    # New version of length which can handle NA's: if na.rm==T, don't count them
    length2 <- function (x, na.rm=FALSE) {
        if (na.rm) sum(!is.na(x))
        else       length(x)
    }

    # Collapse the data
    formula <- as.formula(paste(measurevar, paste(groupvars, collapse=" + "), sep=" ~ "))
    datac <- summaryBy(formula, data=data, FUN=c(length2,mean,sd), na.rm=na.rm)

    # Rename columns
    names(datac)[ names(datac) == paste(measurevar, ".mean",    sep="") ] <- measurevar
    names(datac)[ names(datac) == paste(measurevar, ".sd",      sep="") ] <- "sd"
    names(datac)[ names(datac) == paste(measurevar, ".length2", sep="") ] <- "N"
    
    datac$se <- datac$sd / sqrt(datac$N)  # Calculate standard error of the mean
    
    # Confidence interval multiplier for standard error
    # Calculate t-statistic for confidence interval: 
    # e.g., if conf.interval is .95, use .975 (above/below), and use df=N-1
    ciMult <- qt(conf.interval/2 + .5, datac$N-1)
    datac$ci <- datac$se * ciMult
    
    return(datac)
}
```


```{r GR plot mean plus error energy used}

summary_snake<-summarySE(all_snake, measurevar = "ED_per_used", groupvars = c( "scenario"))

summary_GR<-summarySE(all_GR, measurevar = "ED_per_used", groupvars = c( "scenario"))

```

```{r SR plot mean plus error energy used}
ggplot(summary_snake, aes(x=scenario, y=ED_per_used, colour=scenario, fill=scenario)) +
  geom_errorbar(aes(ymin=ED_per_used - sd, ymax=ED_per_used + sd), width = 0.1) +
  geom_point() + 
  xlab("Scenario") + ylab("% Energy Density Used")

ggplot(summary_GR, aes(x=scenario, y=ED_per_used, colour=scenario, fill=scenario)) +
  geom_errorbar(aes(ymin=ED_per_used - sd, ymax=ED_per_used + sd), width = 0.1) +
  geom_point() + 
  xlab("Scenario") + ylab("% Energy Density Used")
```



```{r}
# combine snake and GR dataframes
all_energy<-rbind.data.frame(all_snake, all_GR)

# for text wrapping
var_width = 15
all_energy <- mutate(all_energy, pretty_scenario = stringr::str_wrap(scenario, width = var_width))

# create summary stats
summary_all<-summarySE(all_energy, measurevar = "ED_per_used", groupvars = c( "pretty_scenario", "Population"))

# for plot position dodging
pd <- position_dodge(0.1) # move them .05 to the left and right

width1 = 4
height1 = 3
png("C:/Users/msnyde02/OneDrive - Environmental Protection Agency (EPA)/Profile/Desktop/Manuscript CWR Columbia/GR_SR_energy_used.png", res=300, width=width1, height=height1, units="in", type="windows", antialias = "none")

# plot
ggplot(summary_all, aes(x=pretty_scenario, y=ED_per_used, colour=Population, fill=Population)) +
  geom_errorbar(aes(ymin=ED_per_used - sd, ymax=ED_per_used + sd), width = 0.1, position=pd) +
  geom_point(position=pd) + 
  ylab("% Energy Density Used")+ xlab("")+
 scale_color_manual(breaks=c("Chinook", "Steelhead"), values=c("green", "purple"))+
  theme_classic(base_size=10) + 
  theme(legend.position = "none")

dev.off()
```




