---
title: "GR and SR 2D HDR Plots"
author: "MNSnyder"
date: "1/29/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(cowplot)
library(data.table)
library(knitr)
library(chron)
library(lubridate)
library(dplyr)
library(plotly)
library(GGally)
library(doBy) # statistical summary function
library(stringr)
library(hdrcde)
```

Imports end condition data for combined replicates for 2 populations (Snake River Fall Chinook and Grande Ronde summer steelhead) for 4 scenarios which vary by thermalscape- 
* Columbia 2017
* Columbia 2017, no CWRs
* Columbia 2017 + 1 degree
* Columbia 2017 + 1 degree, no CWRs

Creates a number of exploratory plots looking at how successful migration strategies decrease. 

Ultimately used to create a faceted by scenario 2D HDR plot with smoothing showing how the successful migration strategy trait spaces contracts without CWRS and with hotter Columbia River temperatures. Migration strategy is characterized by entry timing related to the date of the maximum Columbia River temperature and the migration speed of individuals outside of CWRs (reservoir hours). 


###################################
Statistical Summary function

```{r statistical summary function}
## Summarizes data.
## Gives count, mean, standard deviation, standard error of the mean, and confidence 
## interval (default 95%).
##   data: a data frame.
##   measurevar: the name of a column that contains the variable to be summariezed
##   groupvars: a vector containing names of columns that contain grouping variables
##   na.rm: a boolean that indicates whether to ignore NA's
##   conf.interval: the percent range of the confidence interval (default is 95%)
summarySE <- function(data=NULL, measurevar, groupvars=NULL, na.rm=FALSE, conf.interval=.95) {
    library(doBy)

    # New version of length which can handle NA's: if na.rm==T, don't count them
    length2 <- function (x, na.rm=FALSE) {
        if (na.rm) sum(!is.na(x))
        else       length(x)
    }

    # Collapse the data
    formula <- as.formula(paste(measurevar, paste(groupvars, collapse=" + "), sep=" ~ "))
    datac <- summaryBy(formula, data=data, FUN=c(length2,mean,sd), na.rm=na.rm)

    # Rename columns
    names(datac)[ names(datac) == paste(measurevar, ".mean",    sep="") ] <- measurevar
    names(datac)[ names(datac) == paste(measurevar, ".sd",      sep="") ] <- "sd"
    names(datac)[ names(datac) == paste(measurevar, ".length2", sep="") ] <- "N"
    
    datac$se <- datac$sd / sqrt(datac$N)  # Calculate standard error of the mean
    
    # Confidence interval multiplier for standard error
    # Calculate t-statistic for confidence interval: 
    # e.g., if conf.interval is .95, use .975 (above/below), and use df=N-1
    ciMult <- qt(conf.interval/2 + .5, datac$N-1)
    datac$ci <- datac$se * ciMult
    
    return(datac)
}
```

#################################
Import end condition data for 4 scenarios

```{r GR import end condition data, eval=TRUE}
# import in combined replicate DFs
A13<-read.table("D:/Results_4Populations/gr_Columbia2017B/combined/E13.csv", header=TRUE, sep=",")
B13<-read.table("D:/Results_4Populations/gr_Columbia2017B_NoCWR/combined/F13.csv", header=TRUE, sep=",")
C13<-read.table("D:/Results_4Populations/gr_Columbia2017BplusOne/combined/G13.csv", header=TRUE, sep=",")
D13<-read.table("D:/Results_4Populations/gr_Columbia2017BplusOne_NoCWR/combined/H13.csv", header=TRUE, sep=",")

# rename DF columns
names(A13)<-c("Run", "Step", "Population", "ID", "Time_entry", "Time_exit", "Time_in_system", "Time_remaining", "Total_hours_cold_water", "Initial_weight", "Initial_energy_density", "Fitness_weight", "Fitness_energy_density", "Fitness_energy")
names(B13)<-c("Run", "Step", "Population", "ID", "Time_entry", "Time_exit", "Time_in_system", "Time_remaining", "Total_hours_cold_water", "Initial_weight", "Initial_energy_density", "Fitness_weight", "Fitness_energy_density", "Fitness_energy")
names(C13)<-c("Run", "Step", "Population", "ID", "Time_entry", "Time_exit", "Time_in_system", "Time_remaining", "Total_hours_cold_water", "Initial_weight", "Initial_energy_density", "Fitness_weight", "Fitness_energy_density", "Fitness_energy")
names(D13)<-c("Run", "Step", "Population", "ID", "Time_entry", "Time_exit", "Time_in_system", "Time_remaining", "Total_hours_cold_water", "Initial_weight", "Initial_energy_density", "Fitness_weight", "Fitness_energy_density", "Fitness_energy")

```

```{r SR import end condition data, eval=TRUE}
# import in combined replicate DFs
E4<-read.table("D:/Results_4Populations/snake_Columbia2017B/combined/E4.csv", header=TRUE, sep=",")
F4<-read.table("D:/Results_4Populations/snake_Columbia2017B_NoCWR/combined/F4.csv", header=TRUE, sep=",")
G4<-read.table("D:/Results_4Populations/snake_Columbia2017BplusOne/combined/G4.csv", header=TRUE, sep=",")
H4<-read.table("D:/Results_4Populations/snake_Columbia2017BplusOne_NoCWR/combined/H4.csv", header=TRUE, sep=",")

# rename DF columns
names(E4)<-c("Run", "Step", "Population", "ID", "Time_entry", "Time_exit", "Time_in_system", "Time_remaining", "Total_hours_cold_water", "Initial_weight", "Initial_energy_density", "Fitness_weight", "Fitness_energy_density", "Fitness_energy")
names(F4)<-c("Run", "Step", "Population", "ID", "Time_entry", "Time_exit", "Time_in_system", "Time_remaining", "Total_hours_cold_water", "Initial_weight", "Initial_energy_density", "Fitness_weight", "Fitness_energy_density", "Fitness_energy")
names(G4)<-c("Run", "Step", "Population", "ID", "Time_entry", "Time_exit", "Time_in_system", "Time_remaining", "Total_hours_cold_water", "Initial_weight", "Initial_energy_density", "Fitness_weight", "Fitness_energy_density", "Fitness_energy")
names(H4)<-c("Run", "Step", "Population", "ID", "Time_entry", "Time_exit", "Time_in_system", "Time_remaining", "Total_hours_cold_water", "Initial_weight", "Initial_energy_density", "Fitness_weight", "Fitness_energy_density", "Fitness_energy")
```


#######################################
Import temperature data
```{r import temp table and format, eval=TRUE, include=FALSE}
# import table of water temperatures
water_temps<-read.table("D:/HexSim_Models/CWR_Columbia/Columbia [small]/Analysis/Data Lookup/Columbia2017B_TribsCurrent.csv", header = FALSE, sep = ",")

```

#####################
Format data
```{r format temperature data}
# first row is bonneville teemperature, drop all rows except first
bonn_temp<-water_temps[2,]
bonn_temp2<-t(bonn_temp) # transpose to long
colnames(bonn_temp2)<-"bonn_temp" # change column name
# add column for time step
timestep<-seq(from=1,to=dim(bonn_temp2)[1],by=1) # create sequence for number of hours of temp
#timestep<-seq(from=1, to=2928, by=1)
temp<-cbind.data.frame(bonn_temp2, timestep)
# convert from factor to numeric
temp$bonn_temp <- as.numeric(as.character(temp$bonn_temp))
plot(bonn_temp2~timestep, data=temp, ylab="Bonneville Temperature", xlab=c("Model hour"))
```


```{r get maximum Bonneville temperature hour}
# figure out what hottest temperature is
max_temp<-max(temp$bonn_temp)
# leave only hours in DF with highest temperature
all_max_temps<-dplyr::filter(temp, bonn_temp2 == max_temp)
# choose latest model hour of max temp
row_no<-dim(all_max_temps)[1]
max_temp_hour<-all_max_temps$timestep[4]
```


Create function to calculate:
* Entry Timing
* Total_hours_cold_water
* time in system not in CWR = ReservoirH
* Initial weight

```{r function to calculate end condition metrics}

# function to calculate cumulative degree days above a certain degree

avail_energy_diff<-function(DF){
  DF$gamete<-(((7598 + (0.527 * DF$Initial_weight)) * DF$Initial_weight) * 0.068) / DF$Initial_weight
DF$initial_ED_avail<-DF$Initial_energy_density-DF$gamete
# create column of energy lost
# energy_all$energy_lost<-energy_all$X11 - energy_all$X13
DF$energy_lost_gamete<-(DF$initial_ED_avail - DF$Fitness_energy) 
DF$ED_per_used<-(DF$energy_lost_gamete/DF$initial_ED_avail) * 100
return(DF)
}

# entry timing as related to maximum water temperature function

entry_timing_f <- function(DF, temp_data){
  # figure out what hottest temperature is
  max_temp<-max(temp_data$bonn_temp)
  # leave only hours in DF with highest temperature
  all_max_temps<-dplyr::filter(temp_data, bonn_temp2 == max_temp)
  # choose latest model hour of max temp
  row_no<-dim(all_max_temps)[1]
  # select one max temperature hour
  max_temp_hour<-all_max_temps$timestep[row_no]
  # get entry time value
  DF$EntryTiming<-DF$Time_entry - max_temp_hour
  #DF$EntryPeriod<-ifelse(DF$Time_entry < 1000, "A", ifelse(DF$Time_entry > 1800), "C", "B")
  #as.factor(DF$EntryPeriod)
  return(DF)
}

# combine functions into one function

calculate_metrics <- function(DF, temp_data){
  # calculate entry timing
  A<-entry_timing_f(DF, temp_data)
  # select columns
  A_minus<-select(A, ID, EntryTiming)
  
  # calculate time in system outside CWR
  DF$ReservoirH <- DF$Time_in_system - DF$Total_hours_cold_water
  # rename total hours in CWR column
  DF<-rename(DF, cwrH = Total_hours_cold_water)
  # drop unnecessary columns
  B_minus<-select(DF, ID, ReservoirH, cwrH, Initial_weight)
  
  # calculate % energy density lost
  C<-avail_energy_diff(DF)
  # drop unnecessary columns
  C_minus<-select(C, ID, ED_per_used)
  
  # combine for final data
  out1<-merge(A_minus, B_minus, by.x="ID", by.y="ID")
  metrics_all<-merge(out1, C_minus, by.x="ID", by.y="ID")
  
  return(metrics_all)
}


```


```{r GR calculate metrics}

A_end <- calculate_metrics(A13, temp)
A_end$scenario <- "Current with CWRs"

B_end <- calculate_metrics(B13, temp)
B_end$scenario <- "Current without CWRs"

C_end <- calculate_metrics(C13, temp)
C_end$scenario <- "Future with CWRs"

D_end <- calculate_metrics(D13, temp)
D_end$scenario <- "Future without CWRs"

# combine all scenarios
abcd_end<-rbind.data.frame(A_end, B_end, C_end, D_end)
# convert scenario to factor
abcd_end$scenario <- as.factor(abcd_end$scenario)

# create winners
abcd_win<-filter(abcd_end, ED_per_used < 25)
```


```{r SR calculate metrics}

E_end <- calculate_metrics(E4, temp)
E_end$scenario <- "Current with CWRs"

F_end <- calculate_metrics(F4, temp)
F_end$scenario <- "Current without CWRs"

G_end <- calculate_metrics(G4, temp)
G_end$scenario <- "Future with CWRs"

H_end <- calculate_metrics(H4, temp)
H_end$scenario <- "Future without CWRs"

# combine all scenarios
efgh_end<-rbind.data.frame(E_end, F_end, G_end, H_end)
# convert scenario to factor
efgh_end$scenario <- as.factor(efgh_end$scenario)

# create winners
# 25% quantile = 17.1% energy lost

efgh_win<-filter(efgh_end, ED_per_used < 17)
```



```{r 2D HDR plots}
#x <- c(rnorm(200,0,1),rnorm(200,4,1))
#y <- c(rnorm(200,0,1),rnorm(200,4,1))
#hdr.boxplot.2d(x,y)

# sthd
a_win_sthd<-filter(abcd_win, scenario == "Current with CWRs")
b_win_sthd<-filter(abcd_win, scenario == "Current without CWRs")
c_win_sthd<-filter(abcd_win, scenario == "Future with CWRs")
d_win_sthd<-filter(abcd_win, scenario == "Future without CWRs")
# chnk
a_win_chnk<-filter(efgh_win, scenario == "Current with CWRs")
b_win_chnk<-filter(efgh_win, scenario == "Current without CWRs")
c_win_chnk<-filter(efgh_win, scenario == "Future with CWRs")
d_win_chnk<-filter(efgh_win, scenario == "Future without CWRs")

width1 = 2.75
height1 = 5

# 1. sthd 2017 with CWR
png("C:/Users/msnyde02/OneDrive - Environmental Protection Agency (EPA)/Profile/Desktop/Manuscript CWR Columbia/draft figures/2DHDR/GR_migration_strategy_hdrA.png", res=300, width=width1, height=height1, units="in", type="windows", antialias = "none")
par(xaxt="n", las=1)
lablist.x<-as.vector(seq(-1000,1000, 500))
xtick<-seq(-1000, 1000, by=500)

hdr.boxplot.2d(prob = c(50, 90, 95), x=a_win_sthd$EntryTiming, y=a_win_sthd$ReservoirH, ylab="Migration Time (Outside Cold Water Refuges)", ylim=c(200, 600))
axis(side=1, at=lablist.x,labels=FALSE, tick=TRUE, lwd.ticks=3)
text(x = seq(-1000, 1000, by=500), par("usr")[3] - 10, labels = lablist.x, srt = 45, pos = 1, xpd = TRUE)

dev.off()

# 2. sthd 2017 no CWR
png("C:/Users/msnyde02/OneDrive - Environmental Protection Agency (EPA)/Profile/Desktop/Manuscript CWR Columbia/draft figures/2DHDR/GR_migration_strategy_hdrB.png", res=300, width=width1, height=height1, units="in", type="windows", antialias = "none")
par(xaxt="n", las=1)
lablist.x<-as.vector(seq(-1000,1000, 500))
xtick<-seq(-1000, 1000, by=500)

hdr.boxplot.2d(prob = c(50, 90, 95), x=b_win_sthd$EntryTiming, y=b_win_sthd$ReservoirH, ylab="Migration Time (Outside Cold Water Refuges)", ylim=c(200, 600))
axis(side=1, at=lablist.x,labels=FALSE, tick=TRUE, lwd.ticks=3)
text(x = seq(-1000, 1000, by=500), par("usr")[3] - 10, xtick, labels = lablist.x, srt = 45, pos = 1, xpd = TRUE)

dev.off()

# 3. sthd 2040 w CWR
png("C:/Users/msnyde02/OneDrive - Environmental Protection Agency (EPA)/Profile/Desktop/Manuscript CWR Columbia/draft figures/2DHDR/GR_migration_strategy_hdrC.png", res=300, width=width1, height=height1, units="in", type="windows", antialias = "none")
par(xaxt="n", las=1)
lablist.x<-as.vector(seq(-1000,1000, 500))
xtick<-seq(-1000, 1000, by=500)

hdr.boxplot.2d(prob = c(50, 90, 95), x=c_win_sthd$EntryTiming, y=c_win_sthd$ReservoirH, ylab="Migration Time (Outside Cold Water Refuges)", ylim=c(200, 600))
axis(side=1, at=lablist.x,labels=FALSE, tick=TRUE, lwd.ticks=3)
text(x = seq(-1000, 1000, by=500), par("usr")[3] - 10, xtick, labels = lablist.x, srt = 45, pos = 1, xpd = TRUE)

dev.off()

# 4. sthd no CWR
png("C:/Users/msnyde02/OneDrive - Environmental Protection Agency (EPA)/Profile/Desktop/Manuscript CWR Columbia/draft figures/2DHDR/GR_migration_strategy_hdrD.png", res=300, width=width1, height=height1, units="in", type="windows", antialias = "none")
par(xaxt="n", las=1)
lablist.x<-as.vector(seq(-1000,1000, 500))
xtick<-seq(-1000, 1000, by=500)

hdr.boxplot.2d(prob = c(50, 90, 95), x=d_win_sthd$EntryTiming, y=d_win_sthd$ReservoirH, ylab="Migration Time (Outside Cold Water Refuges)", ylim=c(200, 600))
axis(side=1, at=lablist.x,labels=FALSE, tick=TRUE, lwd.ticks=3)
text(x = seq(-1000, 1000, by=500), par("usr")[3] - 10, xtick, labels = lablist.x, srt = 45, pos = 1, xpd = TRUE)

dev.off()

#### one with tick marks
png("C:/Users/msnyde02/OneDrive - Environmental Protection Agency (EPA)/Profile/Desktop/Manuscript CWR Columbia/draft figures/2DHDR/GR_migration_strategy_hdr_tick.png", res=300, width=width1, height=height1, units="in", type="windows", antialias = "none")

lablist.x<-as.vector(seq(-1000,1000, 500))
xtick<-seq(-1000, 1000, by=500)

hdr.boxplot.2d(prob = c(50, 90, 95), x=d_win_sthd$EntryTiming, y=d_win_sthd$ReservoirH, ylab="Migration Time (Outside Cold Water Refuges)", ylim=c(200, 600))
axis(side=1, at=lablist.x,labels=FALSE, tick=TRUE, lwd.ticks=3)
text(x = seq(-1000, 1000, by=500), par("usr")[3] - 10, xtick, labels = lablist.x, srt = 45, pos = 1, xpd = TRUE)

dev.off()

################################
## chnk
# 1. chnk 2017 with CWR


png("C:/Users/msnyde02/OneDrive - Environmental Protection Agency (EPA)/Profile/Desktop/Manuscript CWR Columbia/draft figures/2DHDR/SR_migration_strategy_hdrE.png", res=300, width=width1, height=height1, units="in", type="windows", antialias = "none")
par(xaxt="n", yaxt='n',las=1)
#lablist.x<-as.vector(seq(-500,1000, 500))
#xtick<-seq(-500, 1000, by=500)

hdr.boxplot.2d(prob = c(50, 90, 95), x=a_win_chnk$EntryTiming, y=a_win_chnk$ReservoirH, ylab="Migration Time (Outside Cold Water Refuges)", ylim=c(100, 400), xlim=c(-300,1000))
#axis(side=1, at=lablist.x,labels=FALSE, tick=TRUE, lwd.ticks=3)
#text(x = seq(-500, 1000, by=500), par("usr")[3] - 10, xtick, labels = lablist.x, srt = 45, pos = 1, xpd = TRUE)

dev.off()

# 2. chnk 2017 no CWR
png("C:/Users/msnyde02/OneDrive - Environmental Protection Agency (EPA)/Profile/Desktop/Manuscript CWR Columbia/draft figures/2DHDR/SR_migration_strategy_hdrF.png", res=300, width=width1, height=height1, units="in", type="windows", antialias = "none")
par(xaxt="n", yaxt='n',las=1)
#lablist.x<-as.vector(seq(-500,1000, 500))
#xtick<-seq(-500, 1000, by=500)

hdr.boxplot.2d(prob = c(50, 90, 95), x=b_win_chnk$EntryTiming, y=b_win_chnk$ReservoirH, ylab="Migration Time (Outside Cold Water Refuges)", ylim=c(100, 400), xlim=c(-300,1000))
#axis(side=1, at=lablist.x,labels=FALSE, tick=TRUE, lwd.ticks=3)
#text(x = seq(-500, 1000, by=500), par("usr")[3] - 10, xtick, labels = lablist.x, srt = 45, pos = 1, xpd = TRUE)

dev.off()

# 3. chnk 2040 w CWR
png("C:/Users/msnyde02/OneDrive - Environmental Protection Agency (EPA)/Profile/Desktop/Manuscript CWR Columbia/draft figures/2DHDR/SR_migration_strategy_hdrG.png", res=300, width=width1, height=height1, units="in", type="windows", antialias = "none")
par(xaxt="n",yaxt='n', las=1)
#lablist.x<-as.vector(seq(-500,1000, 500))
#xtick<-seq(-500, 1000, by=500)

hdr.boxplot.2d(prob = c(50, 90, 95), x=c_win_chnk$EntryTiming, y=c_win_chnk$ReservoirH, ylab="Migration Time (Outside Cold Water Refuges)", ylim=c(100, 400), xlim=c(-300,1000))
#axis(side=1, at=lablist.x,labels=FALSE, tick=TRUE, lwd.ticks=3)
#text(x = seq(-500, 1000, by=500), par("usr")[3] - 10, xtick, labels = lablist.x, srt = 45, pos = 1, xpd = TRUE)

dev.off()

# 4. chnk no CWR
png("C:/Users/msnyde02/OneDrive - Environmental Protection Agency (EPA)/Profile/Desktop/Manuscript CWR Columbia/draft figures/2DHDR/SR_migration_strategy_hdrH.png", res=300, width=width1, height=height1, units="in", type="windows", antialias = "none")
par(xaxt="n", yaxt='n', las=1)
#lablist.x<-as.vector(seq(-500,1000, 500))
#xtick<-seq(-500, 1000, by=500)

hdr.boxplot.2d(prob = c(50, 90, 95), x=d_win_chnk$EntryTiming, y=d_win_chnk$ReservoirH, ylab="Migration Time (Outside Cold Water Refuges)", ylim=c(100, 400), xlim=c(-300,1000))
#axis(side=1, at=lablist.x,labels=FALSE, tick=TRUE, lwd.ticks=3)
#text(x = seq(-500, 1000, by=500), par("usr")[3] - 10, xtick, labels = lablist.x, srt = 45, pos = 1, xpd = TRUE)

dev.off()

# 5. chnk tick marks
png("C:/Users/msnyde02/OneDrive - Environmental Protection Agency (EPA)/Profile/Desktop/Manuscript CWR Columbia/draft figures/2DHDR/SR_migration_strategy_hdr_tick.png", res=300, width=width1, height=height1, units="in", type="windows", antialias = "none")
par(las=1)
#lablist.x<-as.vector(seq(-500,1000, 500))
#xtick<-seq(-500, 1000, by=500)

hdr.boxplot.2d(prob = c(50, 90, 95), x=b_win_chnk$EntryTiming, y=b_win_chnk$ReservoirH, ylab="Migration Time (Outside Cold Water Refuges)", ylim=c(100, 400), xlim=c(-300,1000))
#axis(side=1, at=lablist.x,labels=FALSE, tick=TRUE, lwd.ticks=3)
#text(x = seq(-500, 1000, by=500), par("usr")[3] - 10, xtick, labels = lablist.x, srt = 45, pos = 1, xpd = TRUE)

dev.off()


# png("C:/Users/msnyde02/OneDrive - Environmental Protection Agency (EPA)/Profile/Desktop/Manuscript CWR Columbia/SR_migration_strategy_hdr.png", res=300, width=width1, height=height1, units="in", type="windows", antialias = "none")
# # chnk
# par(mfrow=c(2,2), mar=c(2,2,1,1)) # (bottom, left, top, right)
# hdr.boxplot.2d(prob = c(50, 90, 95), x=a_win_chnk$EntryTiming, y=a_win_chnk$ReservoirH, ylab="Migration Time outside CWRs", ylim=c(100, 400))
# hdr.boxplot.2d(prob = c(50, 90, 95), x=b_win_chnk$EntryTiming, y=b_win_chnk$ReservoirH, ylim=c(100, 400))
# hdr.boxplot.2d(prob = c(50, 90, 95), x=c_win_chnk$EntryTiming, y=c_win_chnk$ReservoirH, xlab="Entry Time (in relation to maximum temperature)", ylab="Migration Time outside CWRs", ylim=c(100, 400))
# hdr.boxplot.2d(prob = c(50, 90, 95), x=d_win_chnk$EntryTiming, y=d_win_chnk$ReservoirH, xlab="Entry Time (in relation to maximum temperature)", ylim=c(100, 400))
# dev.off()



#par(mfrow=c(1,2))
#hdr.boxplot.2d(x=abcd_end$EntryTiming, y=abcd_end$ReservoirH)
#hdr.boxplot.2d(x=abcd_win$EntryTiming, y=abcd_win$ReservoirH)

hdr.boxplot.2d(x=efgh_end$EntryTiming, y=efgh_end$ReservoirH)
hdr.boxplot.2d(x=efgh_win$EntryTiming, y=efgh_win$ReservoirH)


```
