---
title: "Hanford Chinook salmon combine replicates"
author: "MNSnyder"
date: "8/20/2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE)
library(readr)
library(tidyverse)
library(reshape2)
library(ggplot2)
library(knitr)
library(lubridate)
library(plyr)
library(data.table)
```


## Hanford reach Chinook salmon combine replicates. 


Combines Data Probe model outputs for replicate model runs into one DF. Unique ID values are created by concatenating ID value with replicate number. 

Need to specify path to individual replicate for a HexSim model run. 

## Columbia 2040 Current CWR
```{r Columbia 2040 Current CWR set up path to each replicate model run}
path1<-"D:/Results_4Populations/hanford_Columbia2040_current/hanford_Columbia2040_current-[1]/Data Probe/"
path2<-"D:/Results_4Populations/hanford_Columbia2040_current/hanford_Columbia2040_current-[2]/Data Probe/"
path3<-"D:/Results_4Populations/hanford_Columbia2040_current/hanford_Columbia2040_current-[3]/Data Probe/"

```

For each replicate imports all CSVs in Data Probe folder into a list of tibbles. Each path defined above needs to be specified below to read in CSVs and create new unique ID.
```{r Columbia 2040 Current CWR create unique ID for each CSV for replicates}
## creates a list of tibbles of all CSVs in directory
files1 <- list.files(path = path1, pattern = '.csv$', full.names = T) %>%
  map(read_csv)
#adds a new ID column with original ID and replicate concatenated
for (e in 1:length(files1)){
   files1[[e]]$test1<-rep(1, length(files1[[e]]$ID))
   files1[[e]]$test<-paste(files1[[e]]$ID,files1[[e]]$test1, sep="_")
  }

##
files2 <- list.files(path = path2, pattern = '.csv$', full.names = T) %>%
  map(read_csv)
# adds a new ID column with original ID and replicate concatenated
for (e in 1:length(files2)){
  files2[[e]]$test1<-rep(2, length(files2[[e]]$ID))
  files2[[e]]$test<-paste(files2[[e]]$ID,files2[[e]]$test1, sep="_")
}

##
files3 <- list.files(path = path3, pattern = '.csv$', full.names = T) %>%
  map(read_csv)
# adds a new ID column with original ID and replicate concatenated
for (e in 1:length(files3)){
  files3[[e]]$test1<-rep(3, length(files3[[e]]$ID))
  files3[[e]]$test<-paste(files3[[e]]$ID,files3[[e]]$test1, sep="_")
}

```

Need to specify lists to be combined below (files1, files2, files3). Drops intermediate columns used to create unique ID and re-orders columns to match original order of columns.
```{r Columbia 2040 Current CWR combine like replicate DFs from lists into individual DFs}
#### combine tibbles from different lists into DF ####
# creates DF A1 through A17
# create combined folder before running
dir.create("D:/Results_4Populations/hanford_Columbia2040_current/combined/")
setwd("D:/Results_4Populations/hanford_Columbia2040_current/combined/")

for (f in 1:length(files1)){
  nam <- paste("A", f, sep = "")
  outDF<-rbind(files1[[f]], files2[[f]],  files3[[f]]) # combine tibbles from different lists into DF
  outDF2<-select(outDF, -test1, -ID) # drop intermediate columns
  outDF2<-dplyr::rename(outDF2, ID=test) # rename new ID column
  outDF2<-select(outDF2, Run, Step, Population, ID, everything()) # put new ID column in same location as old
  assign(nam, outDF2) # name DF based on order in CSV list
  fwrite(outDF2, file=paste0(nam, ".csv"),   sep = ",")
  }
```

## Columbia Restored CWR Current
```{r Columbia Restored CWR Current set up path to each replicate model run}
path4<-"D:/Results_4Populations/hanford_Columbiarestored_CWRcurrent/hanford_Columbiarestored_CWRcurrent-[1]/Data Probe/"
path5<-"D:/Results_4Populations/hanford_Columbiarestored_CWRcurrent/hanford_Columbiarestored_CWRcurrent-[2]/Data Probe/"
path6<-"D:/Results_4Populations/hanford_Columbiarestored_CWRcurrent/hanford_Columbiarestored_CWRcurrent-[3]/Data Probe/"

```

For each replicate imports all CSVs in Data Probe folder into a list of tibbles. Each path defined above needs to be specified below to read in CSVs and create new unique ID.
```{r Columbia Restored CWR Current create unique ID for each CSV for replicates}
## creates a list of tibbles of all CSVs in directory
files1 <- list.files(path = path4, pattern = '.csv$', full.names = T) %>%
  map(read_csv)
#adds a new ID column with original ID and replicate concatenated
for (e in 1:length(files1)){
   files1[[e]]$test1<-rep(1, length(files1[[e]]$ID))
   files1[[e]]$test<-paste(files1[[e]]$ID,files1[[e]]$test1, sep="_")
  }

##
files2 <- list.files(path = path5, pattern = '.csv$', full.names = T) %>%
  map(read_csv)
# adds a new ID column with original ID and replicate concatenated
for (e in 1:length(files2)){
  files2[[e]]$test1<-rep(2, length(files2[[e]]$ID))
  files2[[e]]$test<-paste(files2[[e]]$ID,files2[[e]]$test1, sep="_")
}

##
files3 <- list.files(path = path6, pattern = '.csv$', full.names = T) %>%
  map(read_csv)
# adds a new ID column with original ID and replicate concatenated
for (e in 1:length(files3)){
  files3[[e]]$test1<-rep(3, length(files3[[e]]$ID))
  files3[[e]]$test<-paste(files3[[e]]$ID,files3[[e]]$test1, sep="_")
}

```

Need to specify lists to be combined below (files1, files2, files3). Drops intermediate columns used to create unique ID and re-orders columns to match original order of columns.
```{r Columbia Restored CWR Current combine like replicate DFs from lists into individual DFs}
#### combine tibbles from different lists into DF ####
dir.create("D:/Results_4Populations/hanford_Columbiarestored_CWRcurrent/combined/")
setwd("D:/Results_4Populations/hanford_Columbiarestored_CWRcurrent/combined/")

for (f in 1:length(files1)){
  nam <- paste("B", f, sep = "")
  outDF<-rbind(files1[[f]], files2[[f]],  files3[[f]]) # combine tibbles from different lists into DF
  outDF2<-select(outDF, -test1, -ID) # drop intermediate columns
  outDF2<-dplyr::rename(outDF2, ID=test) # rename new ID column
  outDF2<-select(outDF2, Run, Step, Population, ID, everything()) # put new ID column in same location as old
  assign(nam, outDF2) # name DF based on order in CSV list
  fwrite(outDF2, file=paste0(nam, ".csv"),   sep = ",")
  }
```

## Columbia Current CWR Current
```{r Columbia Current CWR Current set up path to each replicate model run}
path7<-"D:/Results_4Populations/hanford_current_current/hanford_current_current-[1]/Data Probe/"
path8<-"D:/Results_4Populations/hanford_current_current/hanford_current_current-[2]/Data Probe/"
path9<-"D:/Results_4Populations/hanford_current_current/hanford_current_current-[3]/Data Probe/"

```

For each replicate imports all CSVs in Data Probe folder into a list of tibbles. Each path defined above needs to be specified below to read in CSVs and create new unique ID.
```{r Columbia Current CWR Current create unique ID for each CSV for replicates}
## creates a list of tibbles of all CSVs in directory
files1 <- list.files(path = path7, pattern = '.csv$', full.names = T) %>%
  map(read_csv)
#adds a new ID column with original ID and replicate concatenated
for (e in 1:length(files1)){
   files1[[e]]$test1<-rep(1, length(files1[[e]]$ID))
   files1[[e]]$test<-paste(files1[[e]]$ID,files1[[e]]$test1, sep="_")
  }

##
files2 <- list.files(path = path8, pattern = '.csv$', full.names = T) %>%
  map(read_csv)
# adds a new ID column with original ID and replicate concatenated
for (e in 1:length(files2)){
  files2[[e]]$test1<-rep(2, length(files2[[e]]$ID))
  files2[[e]]$test<-paste(files2[[e]]$ID,files2[[e]]$test1, sep="_")
}

##
files3 <- list.files(path = path9, pattern = '.csv$', full.names = T) %>%
  map(read_csv)
# adds a new ID column with original ID and replicate concatenated
for (e in 1:length(files3)){
  files3[[e]]$test1<-rep(3, length(files3[[e]]$ID))
  files3[[e]]$test<-paste(files3[[e]]$ID,files3[[e]]$test1, sep="_")
}

```

Need to specify lists to be combined below (files1, files2, files3). Drops intermediate columns used to create unique ID and re-orders columns to match original order of columns.
```{r Columbia Current CWR Current combine like replicate DFs from lists into individual DFs}
#### combine tibbles from different lists into DF ####
dir.create("D:/Results_4Populations/hanford_current_current/combined/")
setwd("D:/Results_4Populations/hanford_current_current/combined/")

for (f in 1:length(files1)){
  nam <- paste("C", f, sep = "")
  outDF<-rbind(files1[[f]], files2[[f]],  files3[[f]]) # combine tibbles from different lists into DF
  outDF2<-select(outDF, -test1, -ID) # drop intermediate columns
  outDF2<-dplyr::rename(outDF2, ID=test) # rename new ID column
  outDF2<-select(outDF2, Run, Step, Population, ID, everything()) # put new ID column in same location as old
  assign(nam, outDF2) # name DF based on order in CSV list
  fwrite(outDF2, file=paste0(nam, ".csv"),   sep = ",")
  }
```


## Columbia Current CWR Restored
```{r Columbia Current CWR Restored set up path to each replicate model run}
path10<-"D:/Results_4Populations/hanford_current_restoredCWR/hanford_current_restoredCWR-[1]/Data Probe/"
path11<-"D:/Results_4Populations/hanford_current_restoredCWR/hanford_current_restoredCWR-[2]/Data Probe/"
path12<-"D:/Results_4Populations/hanford_current_restoredCWR/hanford_current_restoredCWR-[3]/Data Probe/"

```

For each replicate imports all CSVs in Data Probe folder into a list of tibbles. Each path defined above needs to be specified below to read in CSVs and create new unique ID.
```{r Columbia Current CWR Restored create unique ID for each CSV for replicates}
## creates a list of tibbles of all CSVs in directory
files1 <- list.files(path = path10, pattern = '.csv$', full.names = T) %>%
  map(read_csv)
#adds a new ID column with original ID and replicate concatenated
for (e in 1:length(files1)){
   files1[[e]]$test1<-rep(1, length(files1[[e]]$ID))
   files1[[e]]$test<-paste(files1[[e]]$ID,files1[[e]]$test1, sep="_")
  }

##
files2 <- list.files(path = pat11, pattern = '.csv$', full.names = T) %>%
  map(read_csv)
# adds a new ID column with original ID and replicate concatenated
for (e in 1:length(files2)){
  files2[[e]]$test1<-rep(2, length(files2[[e]]$ID))
  files2[[e]]$test<-paste(files2[[e]]$ID,files2[[e]]$test1, sep="_")
}

##
files3 <- list.files(path = path12, pattern = '.csv$', full.names = T) %>%
  map(read_csv)
# adds a new ID column with original ID and replicate concatenated
for (e in 1:length(files3)){
  files3[[e]]$test1<-rep(3, length(files3[[e]]$ID))
  files3[[e]]$test<-paste(files3[[e]]$ID,files3[[e]]$test1, sep="_")
}

```

Need to specify lists to be combined below (files1, files2, files3). Drops intermediate columns used to create unique ID and re-orders columns to match original order of columns. Creates a new folder for output and writes combined replicate DFs into output folder.
```{r Columbia Current CWR Restored combine like replicate DFs from lists into individual DFs}
#### combine tibbles from different lists into DF ####
# creates DF D1 through D17
# create combined folder before running
dir.create("D:/Results_4Populations/hanford_current_restoredCWR/combined/")
setwd("D:/Results_4Populations/hanford_current_restoredCWR/combined/")

for (f in 1:length(files1)){
  nam <- paste("D", f, sep = "")
  outDF<-rbind(files1[[f]], files2[[f]],  files3[[f]]) # combine tibbles from different lists into DF
  outDF2<-select(outDF, -test1, -ID) # drop intermediate columns
  outDF2<-dplyr::rename(outDF2, ID=test) # rename new ID column
  outDF2<-select(outDF2, Run, Step, Population, ID, everything()) # put new ID column in same location as old
  assign(nam, outDF2) # name DF based on order in CSV list
  fwrite(outDF2, file=paste0(nam, ".csv"),   sep = ",")
  }
```

