---
title: "Sensitivity Testing: temperature stress on survival"
author: "MNSnyder"
date: "1/8/2020"
output:
  html_document: default
  pdf_document: default
editor_options:
  chunk_output_type: console
---

To evaluate how uncertainty in the temperature exposure survival relationship influences fish fitness outcomes we ran a sensitivity analysis by decreasing survivorship across all temperatures by 0.5% and 1%. We modeled the Grande Ronde Summer Steelhead population because of their large range in propensity to behaviorally thermoregulate. Sensitivity tests were based on a typical recent temperature year (2017) for the Columbia River. To facilitate comparison of the relative importance of mortality from temperature exposure on fish fitness outcomes we also simulated the thermalscape without cold water refuges as part of the sensitvity analysis. The effect of increasing mortality (decreasing survivorship) from temperature stress was measured on fish fitness outcomes including the percent mortality, overall energy used, and arrival timing at the Snake River confluence. 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE)
library(ggplot2)
library(cowplot)
library(data.table)
library(knitr)
library(chron)
library(lubridate)
library(dplyr)
library(plotly)
library(GGally)
library(doBy) # statistical summary function
library(stringr)
```


```{r import and plot temperature mortality table, fig.cap="Fig. 1. Modeled probability of survivorship based on 24 h mean temperature exposure. The default values used in the migration corridor simulation were developed from InStream User's Manual. To test sensitivity of model outcomes to lethal temperature stress the default modeled values were decreased by 0.5% and 1%. ."}

survival<-read.table("D:/git_repo/Columbia_CWR/Sensitivity/acute temperature mortality/Temperature vs Survival Curves.csv", header=TRUE, sep=",")
survival0.5<-read.table("D:/git_repo/Columbia_CWR/Sensitivity/acute temperature mortality/Temperature vs Survival minus0.5.csv", header=TRUE, sep=",")
survival1<-read.table("D:/git_repo/Columbia_CWR/Sensitivity/acute temperature mortality/Temperature vs Survival minus1.csv", header=TRUE, sep=",")

## format for plot
# rename columns
names(survival) <- c("Temperature", "Survival")
names(survival0.5) <- c("Temperature", "Survival")
names(survival1) <- c("Temperature", "Survival")
# name tests for plot group
survival$scenario <- "Default"
survival0.5$scenario <- "Decrease survival by 0.5%"
survival1$scenario <- "Decrease survival by 1%"
# combine DF into one for plot
survival_all <- rbind.data.frame(survival, survival0.5, survival1)
survival_all$scenario <- as.factor(survival_all$scenario)
# change order of scenarios for plot
survival_all$scenario <- factor(survival_all$scenario, levels=c("Default", "Decrease survival by 0.5%", "Decrease survival by 1%"))

## plot

survival_plot<-ggplot(survival_all, aes(x=Temperature, y=Survival, colour=scenario)) +
  geom_line(size=1.25) +
  scale_color_manual(values = c("blue", "orange", "cyan"))+
  ylab("% Survival (24 h)")+ xlab("Temperature (°C)")+
  theme_bw()+
  theme(legend.title = element_blank())

survival_plot
```



```{r import end condition}
# import in combined replicate DFs
A13<-read.table("D:/Results_4Populations/gr_Columbia2017B/combined/E13.csv", header=TRUE, sep=",")
B13<-read.table("D:/Results_4Populations/gr_Columbia2017B_NoCWR/combined/F13.csv", header=TRUE, sep=",")
C13<-read.table("D:/Results_4Populations/gr_Columbia2017B_minus0.5/combined/E13.csv", header=TRUE, sep=",")
D13<-read.table("D:/Results_4Populations/gr_Columbia2017B_NoCWR_minus0.5/combined/G13.csv", header=TRUE, sep=",")
E13<-read.table("D:/Results_4Populations/gr_Columbia2017B_minus1/combined/F13.csv", header=TRUE, sep=",")
F13<-read.table("D:/Results_4Populations/gr_Columbia2017B_NoCWR_minus1/combined/H13.csv", header=TRUE, sep=",")

# rename columns
rename_end_condition <-function(DF){
  names(DF)<-c("Run", "Step", "Population", "ID", "Time_entry", "Time_exit", "Time_in_system", "Time_remaining", "Total_hours_cold_water", "Initial_weight", "Initial_energy_density", "Fitness_weight", "Fitness_energy_density", "Fitness_energy")
  return(DF)
}

A13 <- rename_end_condition(A13)
B13 <- rename_end_condition(B13)
C13 <- rename_end_condition(C13)
D13 <- rename_end_condition(D13)
E13 <- rename_end_condition(E13)
F13 <- rename_end_condition(F13)

```


```{r created energy used for all scenarios without gamete}
# function to calculate cumulative degree days above a certain degree
avail_energy_diff<-function(DF){
  DF$gamete<-(((7598 + (0.527 * DF$Initial_weight)) * DF$Initial_weight) * 0.068) / DF$Initial_weight
DF$initial_ED_avail<-DF$Initial_energy_density-DF$gamete
# create column of energy lost
# energy_all$energy_lost<-energy_all$X11 - energy_all$X13
DF$energy_lost_gamete<-(DF$initial_ED_avail - DF$Fitness_energy) 
DF$ED_per_used<-(DF$energy_lost_gamete/DF$initial_ED_avail) * 100
return(DF)
}

A13<-avail_energy_diff(A13)
B13<-avail_energy_diff(B13)
C13<-avail_energy_diff(C13)
D13<-avail_energy_diff(D13)
E13<-avail_energy_diff(E13)
F13<-avail_energy_diff(F13)

# add scenario identifying column
A13$scenario<-"Default"
B13$scenario<-"Default without CWRs"
C13$scenario<-"Decrease survival by 0.5%"
D13$scenario<-"Decrease survival by 0.5% without CWRs"
E13$scenario<-"Decrease survival by 1%"
F13$scenario<-"Decrease survival by 1% without CWRs"

# combine DFs 
all_GR<-rbind.data.frame(A13, B13, C13, D13, E13, F13)
```


```{r statistical summary function}
## Summarizes data.
## Gives count, mean, standard deviation, standard error of the mean, and confidence 
## interval (default 95%).
##   data: a data frame.
##   measurevar: the name of a column that contains the variable to be summariezed
##   groupvars: a vector containing names of columns that contain grouping variables
##   na.rm: a boolean that indicates whether to ignore NA's
##   conf.interval: the percent range of the confidence interval (default is 95%)
summarySE <- function(data=NULL, measurevar, groupvars=NULL, na.rm=FALSE, conf.interval=.95) {
    library(doBy)

    # New version of length which can handle NA's: if na.rm==T, don't count them
    length2 <- function (x, na.rm=FALSE) {
        if (na.rm) sum(!is.na(x))
        else       length(x)
    }

    # Collapse the data
    formula <- as.formula(paste(measurevar, paste(groupvars, collapse=" + "), sep=" ~ "))
    datac <- summaryBy(formula, data=data, FUN=c(length2,mean,sd), na.rm=na.rm)

    # Rename columns
    names(datac)[ names(datac) == paste(measurevar, ".mean",    sep="") ] <- measurevar
    names(datac)[ names(datac) == paste(measurevar, ".sd",      sep="") ] <- "sd"
    names(datac)[ names(datac) == paste(measurevar, ".length2", sep="") ] <- "N"
    
    datac$se <- datac$sd / sqrt(datac$N)  # Calculate standard error of the mean
    
    # Confidence interval multiplier for standard error
    # Calculate t-statistic for confidence interval: 
    # e.g., if conf.interval is .95, use .975 (above/below), and use df=N-1
    ciMult <- qt(conf.interval/2 + .5, datac$N-1)
    datac$ci <- datac$se * ciMult
    
    return(datac)
}
```


```{r GR plot mean plus error energy used}
# for text wrapping
var_width = 15
all_GR2 <- mutate(all_GR, pretty_scenario = stringr::str_wrap(scenario, width = var_width))

summary_GR<-summarySE(all_GR2, measurevar = "ED_per_used", groupvars = c( "pretty_scenario"))

```

```{r import dead table for percent dead across scenarios}
# import in combined replicate DFs
A12<-read.table("D:/Results_4Populations/gr_Columbia2017B/combined/E12.csv", header=TRUE, sep=",")
B12<-read.table("D:/Results_4Populations/gr_Columbia2017B_NoCWR/combined/F12.csv", header=TRUE, sep=",")
C12<-read.table("D:/Results_4Populations/gr_Columbia2017B_minus0.5/combined/E12.csv", header=TRUE, sep=",")
D12<-read.table("D:/Results_4Populations/gr_Columbia2017B_NoCWR_minus0.5/combined/G12.csv", header=TRUE, sep=",")
E12<-read.table("D:/Results_4Populations/gr_Columbia2017B_minus1/combined/F12.csv", header=TRUE, sep=",")
F12<-read.table("D:/Results_4Populations/gr_Columbia2017B_NoCWR_minus1/combined/H12.csv", header=TRUE, sep=",")

names_v<-c("Default","Default without CWRs","Decrease survival by 0.5%","Decrease survival by 0.5% without CWRs","Decrease survival by 1%","Decrease survival by 1% without CWRs")

```

#### *Survival*

A small decrease in survival across all temperatures can translate into a disproporionately higher number of deceased fish because the probability of survivorship is calculated every 24 h. 

```{r create percent dead across scenarios kable}
# number of simulated fish
num_fish<-6000
# get number of individuals died from acute temperature stress
acute_A<-((dim(A12)[1])/ num_fish) * 100
acute_B<-((dim(B12)[1])/ num_fish) * 100
acute_C<-((dim(C12)[1])/ num_fish) * 100
acute_D<-((dim(D12)[1])/ num_fish) * 100
acute_E<-((dim(E12)[1])/ num_fish) * 100
acute_F<-((dim(F12)[1])/ num_fish) * 100

acute_v<-c( acute_A, acute_B, acute_C,acute_D, acute_E, acute_F)

acute_all<-cbind.data.frame(names_v, acute_v)

kable(acute_all, digits=1, col.names=c("Scenario", "Total mortality"), caption="Table 1. Model output for percent of individuals dying from acute temperature stress summarized for Grande Ronde River Summer Steelhead.")
```


#### *Energy Use*

```{r percent energy used plot, fig.cap="Fig. 2. Fish fitness model outcomes for the population showing mean (±SE) percent of energy used. To test sensitivity of fish fitness model outcomes to lethal temperature stress the default modeled curve was decreased by 0.5% and 1%. "}

# change order of scenarios for plot
summary_GR$pretty_scenario <- factor(summary_GR$pretty_scenario, levels=c("Default", "Default without\nCWRs", 
                                                      "Decrease\nsurvival by\n0.5%", "Decrease\nsurvival by\n0.5% without\nCWRs",
                                                      "Decrease\nsurvival by 1%", "Decrease\nsurvival by 1%\nwithout CWRs"))


# for plot position dodging
pd <- position_dodge(0.1) # move them .05 to the left and right

width1 = 4
height1 = 3

# plot
ggplot(summary_GR, aes(x=pretty_scenario, y=ED_per_used, colour=pretty_scenario, linetype=pretty_scenario)) +
  geom_errorbar(aes(ymin=ED_per_used - se, ymax=ED_per_used + se), width = 0.1, position=pd, size=1.25) +
  geom_point(position=pd, size=2) + 
  ylab("% Energy Density Used")+ xlab("")+
  theme_classic(base_size=10) + 
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14),legend.position = "none")+ scale_linetype_manual(values=c(1,2,1,2,1,2))+
  scale_colour_manual(values=c("blue4", "blue4", "darkorange3", "darkorange3", "green", "green"))
  
```

#### *Arrival Timing*

```{r arrival timing PDF across scenarios}

# model starts on July 1 which is equivalent to julian day 182
jday_start<-182

# step is hour arrived at terminus
# convert Step to julian day
all_GR2$terminus_jday<-floor(all_GR2$Step / 24) + jday_start
# convert julian day to date
all_GR2$terminus_date_ch<-chron(all_GR2$terminus_jday, origin=c(month=1, day=1, year=2019))
# convert date format to posixct
all_GR2$terminus_date<- as.POSIXct(all_GR2$terminus_date_ch, "GMT") 

# Time_entry is hour started from Bonneville
# convert Step to julian day
all_GR2$entry_jday<-floor(all_GR2$Time_entry / 24) + jday_start
# convert julian day to date
all_GR2$entry_date_ch<-chron(all_GR2$entry_jday, origin=c(month=1, day=1, year=2019))
# convert date format to posixct
all_GR2$entry_date<- as.POSIXct(all_GR2$entry_date_ch, "GMT") 

```


```{r pdf snake river arrival timing, fig.cap="Fig. 3. Smoothed histogram of arrival timing at the Snake River confluence for Grande Ronde River summer steelhead model outputs across six modeled scenarios. To test sensitivity of fish fitness model outcomes to lethal temperature stress the default modeled curve was decreased by 0.5% and 1%. "}
# reorder scenarios for plot
all_GR2$scenario<-as.factor(all_GR2$scenario)
all_GR2$scenario <- factor(all_GR2$scenario, levels=c("Default","Default without CWRs","Decrease survival by 0.5%","Decrease survival by 0.5% without CWRs","Decrease survival by 1%","Decrease survival by 1% without CWRs"))
  
p <- ggplot(data = all_GR2, aes(x = terminus_date, linetype=as.factor(scenario),color=as.factor(scenario))) + geom_density( alpha=0.5, size=1.25) + theme_classic()
p +  labs(x="Exit Day", y="Count", fill="", title="Grande Ronde River Summer Steelhead") +  theme(legend.title = element_blank(), axis.text=element_text(size=14),
        axis.title=element_text(size=14)) +scale_linetype_manual(values=c(1,2,1,2,1,2))+
   scale_color_manual(values=c("blue4", "blue4", "darkorange3", "darkorange3", "green", "green"))
   
```













