---
title: "sensitivity testing probability of CWR use curve"
author: "MNSnyder"
date: "1/8/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

Sensitivity analysis of how move to cold water refuge curve, in the Set Movement Behavior events, affects fish fitness metrics. Increased or decreased the probability of moving to cold water refuge across all the temperatures by (-0.003, -0.006, +0.003, + 0.006) for the whole curve for Grande Ronde River summer steelhead.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(cowplot)
library(data.table)
library(knitr)
library(chron)
library(lubridate)
library(dplyr)
library(plotly)
library(GGally)
library(doBy) # statistical summary function
library(stringr)
```


```{r import and format hourly}
# import in combined replicate DFs
A14<-read.table("D:/Results_4Populations/gr_Columbia2017B_mvmt_minusB/combined/F14.csv", header=TRUE, sep=",")
B14<-read.table("D:/Results_4Populations/gr_Columbia2017B_mvmt_minusA/combined/E14.csv", header=TRUE, sep=",")
C14<-read.table("D:/Results_4Populations/gr_Columbia2017B/combined/E14.csv", header=TRUE, sep=",")
D14<-read.table("D:/Results_4Populations/gr_Columbia2017B_mvmt_plusA/combined/G14.csv", header=TRUE, sep=",")
E14<-read.table("D:/Results_4Populations/gr_Columbia2017B_mvmt_plusB/combined/H14.csv", header=TRUE, sep=",")

# rename hourly column function
rename_hourly_condition <-function(DF){
  names(DF)<-c("Run", "Step", "Population", "ID", "time_entry", "time_exit", "time_in_system", "time_arrived_terminus", "river_km", "motivation", "temp_1", "temp_mean", "energy_density", "weight",
"energy", "selector", "refuge_avoidance", "cwr_hrs_episodic", "cwr_hrs_total", "thermal_patch", "hydropower_location")
  return(DF)
}

# rename columns
A14 <- rename_hourly_condition(A14)
B14 <- rename_hourly_condition(B14)
C14 <- rename_hourly_condition(C14)
D14 <- rename_hourly_condition(D14)
E14 <- rename_hourly_condition(E14)

# add scenario identifying column
A14$scenario<-"Decreased move to CWR by A"
B14$scenario<-"Decreased move to CWR by B"
C14$scenario<-"Current with CWRs"
D14$scenario<-"Increased move to CWR by B"
E14$scenario<-"Increased move to CWR by A"

# combine scenarios
hourly_all <- rbind.data.frame(A14, B14, C14, D14, E14)
```


```{r import temp table, eval=TRUE, include=FALSE}
# import table of water temperatures
water_temps<-read.table("D:/HexSim_Models/CWR_Columbia/Columbia [small]/Analysis/Data Lookup/Columbia2017B_TribsCurrent.csv", header = FALSE, sep = ",")
# first row is bonneville teemperature, drop all rows except first
bonn_temp<-water_temps[2,]
bonn_temp2<-t(bonn_temp) # transpose to long
colnames(bonn_temp2)<-"bonn_temp" # change column name
# add column for time step
timestep<-seq(from=1,to=dim(bonn_temp2)[1],by=1) # create sequence for number of hours of temp
#timestep<-seq(from=1, to=2928, by=1)
temp<-cbind.data.frame(bonn_temp2, timestep)
```


```{r set up data for temp CWR use from bonn to JD, echo=FALSE}
# vector of thermal patch IDs for bonneville to john day
vc <- c(2,3,29,30,31,32,33,34,35,36,37,38,39, 40,41,42,43,44)
# subset hourly data to include patches within the bonneville or dalles pools
hourly_all_subset1<-filter(hourly_all, thermal_patch %in% vc)
# summarize by individual total hours in CWR
hourly_all_subset2<-aggregate(cwr_hrs_total~ID, data=hourly_all_subset1, sum)
# add binary column for if used CWR or no
hourly_all_subset2$refuge_use<-0
hourly_all_subset2$refuge_use[hourly_all_subset2$cwr_hrs_total >12]<-1  
#hourly_all_subset2$refuge_use<-as.factor(hourly_all_subset2$refuge_use)
# aggregate to get one entry per ID for entry_time
ID_entry_time<-aggregate(time_entry~ID+scenario, data=hourly_all,min)
# get time_entry to be used to get entry temp
hourly_all_subset3<-merge(hourly_all_subset2, ID_entry_time,by.x="ID", by.y="ID")
hourly_all_subset3$scenario<-as.factor(hourly_all_subset3$scenario)
# merge with Bonneville temperature dataset
hourly_all_subset4<-merge(hourly_all_subset3, temp, by.x="time_entry", by.y="timestep")
# convert to numeric
hourly_all_subset4$bonn_temp<-as.numeric(as.character(hourly_all_subset4$bonn_temp))
# create categorical temp bins from continuous bonn temps
hourly_all_subset4$cat_temp<-cut(hourly_all_subset4$bonn_temp, breaks=c(-Inf,15,16,17,18,19,20,21,22,23,Inf), labels=c("15","16","17","18","19","20","21","22","23","GT23"))

# get percent refuge use per entry temperature bin
p_refuge_bonn_temp2<-aggregate(refuge_use ~ cat_temp + scenario, data=hourly_all_subset4, mean)

```

```{r}
cwr_use_temp_mod_obs$id<-paste(cwr_use_temp_mod_obs$group, cwr_use_temp_mod_obs$scenario)

p <- ggplot(p_refuge_bonn_temp2, aes(x = cat_temp, y = refuge_use, group=scenario) ) +
        geom_line(size=0.75, aes(linetype=scenario, color=scenario))  +
   labs( y="Percent Refuge Use (BON to JD)", x = "Bonneville Temperature on Entry (?C)") + 
  theme_classic() + 
  theme(axis.text.y = element_text(size=14), 
        axis.text.x=element_text(size=14),
        axis.title.x=element_text(size=14), 
        axis.title.y=element_text(size=14), 
        legend.text = element_text(size=14), 
        legend.title = element_text(size=14))


#+
#  scale_linetype_manual(values=c("solid", "solid","longdash",  "longdash"))+
#     scale_color_manual(values=c("#00FF00", "#6600CC", "#00FF00", "#6600CC"), name="")  
 
p

```

cwr_use_temp_mod_obs$id<-paste(cwr_use_temp_mod_obs$group, cwr_use_temp_mod_obs$species)

p <- ggplot(cwr_use_temp_mod_obs, aes(x = cat_temp, y = refuge_use, group=id) ) +
        geom_line(size=0.75, aes(linetype=id, color=id))  +
   labs( y="Percent Refuge Use (BON to JD)", x = "Bonneville Temperature on Entry (?C)") + 
  theme_classic() + 
  theme(axis.text.y = element_text(size=14), 
        axis.text.x=element_text(size=14),
        axis.title.x=element_text(size=14), 
        axis.title.y=element_text(size=14), 
        legend.text = element_text(size=14), 
        legend.title = element_text(size=14),
        legend.position = "none") +
  scale_linetype_manual(values=c("solid", "solid","longdash",  "longdash"))+
     scale_color_manual(values=c("#00FF00", "#6600CC", "#00FF00", "#6600CC"), name="")  
 
p



```{r import dead table for percent dead across scenarios}
# import in combined replicate DFs
A12<-read.table("D:/Results_4Populations/gr_Columbia2017B_mvmt_minusB/combined/F12.csv", header=TRUE, sep=",")
B12<-read.table("D:/Results_4Populations/gr_Columbia2017B_mvmt_minusA/combined/E12.csv", header=TRUE, sep=",")
C12<-read.table("D:/Results_4Populations/gr_Columbia2017B/combined/E12.csv", header=TRUE, sep=",")
D12<-read.table("D:/Results_4Populations/gr_Columbia2017B_mvmt_plusA/combined/G12.csv", header=TRUE, sep=",")
E12<-read.table("D:/Results_4Populations/gr_Columbia2017B_mvmt_plusB/combined/H12.csv", header=TRUE, sep=",")

names_v <-c("Decreased move to CWR by A", "Decreased move to CWR by B", "Current with CWRs", "Increased move to CWR by B", "Increased move to CWR by A")

```


```{r create percent dead across scenarios kable}
# number of simulated fish
num_fish<-6000
# get number of individuals died from acute temperature stress
acute_A<-((dim(A12)[1])/ num_fish) * 100
acute_B<-((dim(B12)[1])/ num_fish) * 100
acute_C<-((dim(C12)[1])/ num_fish) * 100
acute_D<-((dim(D12)[1])/ num_fish) * 100
acute_E<-((dim(E12)[1])/ num_fish) * 100

acute_v<-c( acute_A, acute_B, acute_C,acute_D, acute_E)

acute_all<-cbind(names_v, acute_v)

kable(acute_all, col.names=c("Scenario", "Total mortality"), digits=2, caption="Table 1. Model output for percent of individuals dying from acute temperature stress summarized for Grande Ronde River Summer Steelhead.")
```


```{r import end condition}
# import in combined replicate DFs
A13<-read.table("D:/Results_4Populations/gr_Columbia2017B_mvmt_minusB/combined/F13.csv", header=TRUE, sep=",")
B13<-read.table("D:/Results_4Populations/gr_Columbia2017B_mvmt_minusA/combined/E13.csv", header=TRUE, sep=",")
C13<-read.table("D:/Results_4Populations/gr_Columbia2017B/combined/E13.csv", header=TRUE, sep=",")
D13<-read.table("D:/Results_4Populations/gr_Columbia2017B_mvmt_plusA/combined/G13.csv", header=TRUE, sep=",")
E13<-read.table("D:/Results_4Populations/gr_Columbia2017B_mvmt_plusB/combined/H13.csv", header=TRUE, sep=",")

# rename columns
rename_end_condition <-function(DF){
  names(DF)<-c("Run", "Step", "Population", "ID", "Time_entry", "Time_exit", "Time_in_system", "Time_remaining", "Total_hours_cold_water", "Initial_weight", "Initial_energy_density", "Fitness_weight", "Fitness_energy_density", "Fitness_energy")
  return(DF)
}

A13 <- rename_end_condition(A13)
B13 <- rename_end_condition(B13)
C13 <- rename_end_condition(C13)
D13 <- rename_end_condition(D13)
E13 <- rename_end_condition(E13)

```


```{r created energy used for all scenarios without gamete}
# function to calculate cumulative degree days above a certain degree
avail_energy_diff<-function(DF){
  DF$gamete<-(((7598 + (0.527 * DF$Initial_weight)) * DF$Initial_weight) * 0.068) / DF$Initial_weight
DF$initial_ED_avail<-DF$Initial_energy_density-DF$gamete
# create column of energy lost
# energy_all$energy_lost<-energy_all$X11 - energy_all$X13
DF$energy_lost_gamete<-(DF$initial_ED_avail - DF$Fitness_energy) 
DF$ED_per_used<-(DF$energy_lost_gamete/DF$initial_ED_avail) * 100
return(DF)
}

A13<-avail_energy_diff(A13)
B13<-avail_energy_diff(B13)
C13<-avail_energy_diff(C13)
D13<-avail_energy_diff(D13)
E13<-avail_energy_diff(E13)

# add scenario identifying column
A13$scenario<-"Decreased move to CWR by A"
B13$scenario<-"Decreased move to CWR by B"
C13$scenario<-"Current with CWRs"
D13$scenario<-"Increased move to CWR by B"
E13$scenario<-"Increased move to CWR by A"

# combine DFs 
all_GR<-rbind.data.frame(A13, B13, C13, D13, E13)
```


```{r statistical summary function}
## Summarizes data.
## Gives count, mean, standard deviation, standard error of the mean, and confidence 
## interval (default 95%).
##   data: a data frame.
##   measurevar: the name of a column that contains the variable to be summariezed
##   groupvars: a vector containing names of columns that contain grouping variables
##   na.rm: a boolean that indicates whether to ignore NA's
##   conf.interval: the percent range of the confidence interval (default is 95%)
summarySE <- function(data=NULL, measurevar, groupvars=NULL, na.rm=FALSE, conf.interval=.95) {
    library(doBy)

    # New version of length which can handle NA's: if na.rm==T, don't count them
    length2 <- function (x, na.rm=FALSE) {
        if (na.rm) sum(!is.na(x))
        else       length(x)
    }

    # Collapse the data
    formula <- as.formula(paste(measurevar, paste(groupvars, collapse=" + "), sep=" ~ "))
    datac <- summaryBy(formula, data=data, FUN=c(length2,mean,sd), na.rm=na.rm)

    # Rename columns
    names(datac)[ names(datac) == paste(measurevar, ".mean",    sep="") ] <- measurevar
    names(datac)[ names(datac) == paste(measurevar, ".sd",      sep="") ] <- "sd"
    names(datac)[ names(datac) == paste(measurevar, ".length2", sep="") ] <- "N"
    
    datac$se <- datac$sd / sqrt(datac$N)  # Calculate standard error of the mean
    
    # Confidence interval multiplier for standard error
    # Calculate t-statistic for confidence interval: 
    # e.g., if conf.interval is .95, use .975 (above/below), and use df=N-1
    ciMult <- qt(conf.interval/2 + .5, datac$N-1)
    datac$ci <- datac$se * ciMult
    
    return(datac)
}
```


```{r GR estimate mean plus error energy used}
# for text wrapping
var_width = 15
all_GR2 <- mutate(all_GR, pretty_scenario = stringr::str_wrap(scenario, width = var_width))

summary_GR<-summarySE(all_GR2, measurevar = "ED_per_used", groupvars = c( "pretty_scenario"))

```


```{r percent energy used plot}
# for plot position dodging
pd <- position_dodge(0.1) # move them .05 to the left and right

width1 = 4
height1 = 3

# plot
ggplot(summary_GR, aes(x=pretty_scenario, y=ED_per_used)) +
  geom_errorbar(aes(ymin=ED_per_used - se, ymax=ED_per_used + se), width = 0.1, position=pd) +
  geom_point(position=pd) + 
  ylab("% Energy Density Used")+ xlab("")+
 #scale_color_manual(breaks=c("Chinook", "Steelhead"), values=c("red", "blue"))+
  theme_classic(base_size=10) + 
  theme(legend.position = "none")
```



```{r arrival timing PDF across scenarios}

# model starts on July 1 which is equivalent to julian day 182
jday_start<-182

# step is hour arrived at terminus
# convert Step to julian day
all_GR2$terminus_jday<-floor(all_GR2$Step / 24) + jday_start
# convert julian day to date
all_GR2$terminus_date_ch<-chron(all_GR2$terminus_jday, origin=c(month=1, day=1, year=2019))
# convert date format to posixct
all_GR2$terminus_date<- as.POSIXct(all_GR2$terminus_date_ch, "GMT") 

# Time_entry is hour started from Bonneville
# convert Step to julian day
all_GR2$entry_jday<-floor(all_GR2$Time_entry / 24) + jday_start
# convert julian day to date
all_GR2$entry_date_ch<-chron(all_GR2$entry_jday, origin=c(month=1, day=1, year=2019))
# convert date format to posixct
all_GR2$entry_date<- as.POSIXct(all_GR2$entry_date_ch, "GMT") 

```


```{r pdf snake river arrival timing}
# reorder scenarios for plot
all_GR2$scenario<-as.factor(all_GR2$scenario)
#all_GR2$scenario <- factor(all_GR2$scenario, levels=c("Decreased move to CWR by A", "Decreased move to CWR by B", "Current with CWRs", "Increased move to CWR by B", "Increased move to CWR by A"))
  
p <- ggplot(data = all_GR2, aes(x = terminus_date, color=scenario)) + geom_density( alpha=0.5, size=1.25) + theme_classic()
p +  labs(x="Exit Day", y="Count", fill="", title="Grande Ronde River Summer Steelhead") +  theme(axis.text=element_text(size=14),
        axis.title=element_text(size=14)) +scale_linetype_manual(values=c(1,2,1,2,1))+
   scale_color_manual(values=c("black", "red", "darkorange3", "darkblue", "cyan"))
   

# p <- ggplot(data = all_GR2, aes(x = terminus_date, linetype=as.factor(scenario),color=as.factor(scenario))) + geom_density( alpha=0.5, size=1.25) + theme_classic()
# p +  labs(x="Exit Day", y="Count", fill="", title="Grande Ronde River Summer Steelhead") +  theme(axis.text=element_text(size=14),
#         axis.title=element_text(size=14)) +scale_linetype_manual(values=c(1,2,1,2,1))+
#    scale_color_manual(values=c("blue4", "blue4", "darkorange3", "darkorange3", "green"))
```

















