---
title: "Combine replicates Snake River fall chinook 2017B acute mortality sensitivity"
author: "MNSnyder"
date: "1/8/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE)
library(readr)
library(tidyverse)
library(reshape2)
library(ggplot2)
library(knitr)
library(lubridate)
library(plyr)
library(data.table)
```


## Grande Ronde River summer steelhead combine replicates. 
Combines repliate output for 4 scenarios- 
* Columbia 2017 with CWRs with modified acute temperature mortality curve +10%
* Columbia 2017 with CWRs with modified acute temperature mortality curve +20%
* Columbia 2017 without CWRs with modified acute temperature mortality curve +10%
* Columbia 2017 without CWRs with modified acute temperature mortality curve +20%


Combines Data Probe model outputs for replicate model runs into one DF. Unique ID values are created by concatenating ID value with replicate number. 

Need to specify path to individual replicate for a HexSim model run. 

## Columbia Current with CWRs acute 10% change
```{r gr_Columbia2017B_acute10 set up path to each replicate model run}
path1<-"D:/Results_4Populations/gr_Columbia2017B_acute10/gr_Columbia2017B_acute10-[1]/Data Probe/"
path2<-"D:/Results_4Populations/gr_Columbia2017B_acute10/gr_Columbia2017B_acute10-[2]/Data Probe/"
path3<-"D:/Results_4Populations/gr_Columbia2017B_acute10/gr_Columbia2017B_acute10-[3]/Data Probe/"

```

For each replicate imports all CSVs in Data Probe folder into a list of tibbles. Each path defined above needs to be specified below to read in CSVs and create new unique ID.
```{r gr_Columbia2017B_acute10 create unique ID for each CSV for replicates}
## creates a list of tibbles of all CSVs in directory
files1 <- list.files(path = path1, pattern = '.csv$', full.names = T) %>%
  map(read_csv)
#adds a new ID column with original ID and replicate concatenated
for (e in 1:length(files1)){
   files1[[e]]$test1<-rep(1, length(files1[[e]]$ID))
   files1[[e]]$test<-paste(files1[[e]]$ID,files1[[e]]$test1, sep="_")
  }

##
files2 <- list.files(path = path2, pattern = '.csv$', full.names = T) %>%
  map(read_csv)
# adds a new ID column with original ID and replicate concatenated
for (e in 1:length(files2)){
  files2[[e]]$test1<-rep(2, length(files2[[e]]$ID))
  files2[[e]]$test<-paste(files2[[e]]$ID,files2[[e]]$test1, sep="_")
}

##
files3 <- list.files(path = path3, pattern = '.csv$', full.names = T) %>%
  map(read_csv)
# adds a new ID column with original ID and replicate concatenated
for (e in 1:length(files3)){
  files3[[e]]$test1<-rep(3, length(files3[[e]]$ID))
  files3[[e]]$test<-paste(files3[[e]]$ID,files3[[e]]$test1, sep="_")
}

```

Need to specify lists to be combined below (files1, files2, files3). Drops intermediate columns used to create unique ID and re-orders columns to match original order of columns.
```{r gr_Columbia2017B_acute10 combine like replicate DFs from lists into individual DFs}
#### combine tibbles from different lists into DF ####
# creates DF A1 through A17
# create combined folder before running
dir.create("D:/Results_4Populations/gr_Columbia2017B_acute10/combined/")
setwd("D:/Results_4Populations/gr_Columbia2017B_acute10/combined/")

for (f in 1:length(files1)){
  nam <- paste("E", f, sep = "")
  outDF<-rbind(files1[[f]], files2[[f]],  files3[[f]]) # combine tibbles from different lists into DF
  outDF2<-select(outDF, -test1, -ID) # drop intermediate columns
  outDF2<-dplyr::rename(outDF2, ID=test) # rename new ID column
  outDF2<-select(outDF2, Run, Step, Population, ID, everything()) # put new ID column in same location as old
  assign(nam, outDF2) # name DF based on order in CSV list
  fwrite(outDF2, file=paste0(nam, ".csv"),   sep = ",")
  }
```

## Columbia Current with CWRs acute 20% change
```{r gr_Columbia2017B_acute20 set up path to each replicate model run}
path4<-"D:/Results_4Populations/gr_Columbia2017B_acute20/gr_Columbia2017B_acute20-[1]/Data Probe/"
path5<-"D:/Results_4Populations/gr_Columbia2017B_acute20/gr_Columbia2017B_acute20-[2]/Data Probe/"
path6<-"D:/Results_4Populations/gr_Columbia2017B_acute20/gr_Columbia2017B_acute20-[3]/Data Probe/"

```

For each replicate imports all CSVs in Data Probe folder into a list of tibbles. Each path defined above needs to be specified below to read in CSVs and create new unique ID.
```{r gr_Columbia2017B_acute20 create unique ID for each CSV for replicates}
## creates a list of tibbles of all CSVs in directory
files1 <- list.files(path = path4, pattern = '.csv$', full.names = T) %>%
  map(read_csv)
#adds a new ID column with original ID and replicate concatenated
for (e in 1:length(files1)){
   files1[[e]]$test1<-rep(1, length(files1[[e]]$ID))
   files1[[e]]$test<-paste(files1[[e]]$ID,files1[[e]]$test1, sep="_")
  }

##
files2 <- list.files(path = path5, pattern = '.csv$', full.names = T) %>%
  map(read_csv)
# adds a new ID column with original ID and replicate concatenated
for (e in 1:length(files2)){
  files2[[e]]$test1<-rep(2, length(files2[[e]]$ID))
  files2[[e]]$test<-paste(files2[[e]]$ID,files2[[e]]$test1, sep="_")
}

##
files3 <- list.files(path = path6, pattern = '.csv$', full.names = T) %>%
  map(read_csv)
# adds a new ID column with original ID and replicate concatenated
for (e in 1:length(files3)){
  files3[[e]]$test1<-rep(3, length(files3[[e]]$ID))
  files3[[e]]$test<-paste(files3[[e]]$ID,files3[[e]]$test1, sep="_")
}

```

Need to specify lists to be combined below (files1, files2, files3). Drops intermediate columns used to create unique ID and re-orders columns to match original order of columns.
```{r gr_Columbia2017B_acute20 combine like replicate DFs from lists into individual DFs}
#### combine tibbles from different lists into DF ####
dir.create("D:/Results_4Populations/gr_Columbia2017B_acute20/combined/")
setwd("D:/Results_4Populations/gr_Columbia2017B_acute20/combined/")

for (f in 1:length(files1)){
  nam <- paste("F", f, sep = "")
  outDF<-rbind(files1[[f]], files2[[f]],  files3[[f]]) # combine tibbles from different lists into DF
  outDF2<-select(outDF, -test1, -ID) # drop intermediate columns
  outDF2<-dplyr::rename(outDF2, ID=test) # rename new ID column
  outDF2<-select(outDF2, Run, Step, Population, ID, everything()) # put new ID column in same location as old
  assign(nam, outDF2) # name DF based on order in CSV list
  fwrite(outDF2, file=paste0(nam, ".csv"),   sep = ",")
  }
```

## Columbia Current without CWRs acute 10% change
```{r gr_Columbia2017B_NoCWR_acute10 set up path to each replicate model run}
path7<-"D:/Results_4Populations/gr_Columbia2017B_NoCWR_acute10/gr_Columbia2017B_NoCWR_acute10-[1]/Data Probe/"
path8<-"D:/Results_4Populations/gr_Columbia2017B_NoCWR_acute10/gr_Columbia2017B_NoCWR_acute10-[2]/Data Probe/"
path9<-"D:/Results_4Populations/gr_Columbia2017B_NoCWR_acute10/gr_Columbia2017B_NoCWR_acute10-[3]/Data Probe/"

```

For each replicate imports all CSVs in Data Probe folder into a list of tibbles. Each path defined above needs to be specified below to read in CSVs and create new unique ID.
```{r gr_Columbia2017B_NoCWR_acute10 create unique ID for each CSV for replicates}
## creates a list of tibbles of all CSVs in directory
files1 <- list.files(path = path7, pattern = '.csv$', full.names = T) %>%
  map(read_csv)
#adds a new ID column with original ID and replicate concatenated
for (e in 1:length(files1)){
   files1[[e]]$test1<-rep(1, length(files1[[e]]$ID))
   files1[[e]]$test<-paste(files1[[e]]$ID,files1[[e]]$test1, sep="_")
  }

##
files2 <- list.files(path = path8, pattern = '.csv$', full.names = T) %>%
  map(read_csv)
# adds a new ID column with original ID and replicate concatenated
for (e in 1:length(files2)){
  files2[[e]]$test1<-rep(2, length(files2[[e]]$ID))
  files2[[e]]$test<-paste(files2[[e]]$ID,files2[[e]]$test1, sep="_")
}

##
files3 <- list.files(path = path9, pattern = '.csv$', full.names = T) %>%
  map(read_csv)
# adds a new ID column with original ID and replicate concatenated
for (e in 1:length(files3)){
  files3[[e]]$test1<-rep(3, length(files3[[e]]$ID))
  files3[[e]]$test<-paste(files3[[e]]$ID,files3[[e]]$test1, sep="_")
}

```

Need to specify lists to be combined below (files1, files2, files3). Drops intermediate columns used to create unique ID and re-orders columns to match original order of columns.
```{r gr_Columbia2017B_NoCWR_acute10 combine like replicate DFs from lists into individual DFs}
#### combine tibbles from different lists into DF ####
dir.create("D:/Results_4Populations/gr_Columbia2017B_NoCWR_acute10/combined/")
setwd("D:/Results_4Populations/gr_Columbia2017B_NoCWR_acute10/combined/")

for (f in 1:length(files1)){
  nam <- paste("G", f, sep = "")
  outDF<-rbind(files1[[f]], files2[[f]],  files3[[f]]) # combine tibbles from different lists into DF
  outDF2<-select(outDF, -test1, -ID) # drop intermediate columns
  outDF2<-dplyr::rename(outDF2, ID=test) # rename new ID column
  outDF2<-select(outDF2, Run, Step, Population, ID, everything()) # put new ID column in same location as old
  assign(nam, outDF2) # name DF based on order in CSV list
  fwrite(outDF2, file=paste0(nam, ".csv"),   sep = ",")
  }
```

## Columbia Current without CWRs acute 20% change
```{r gr_Columbia2017B_NoCWR_acute20 set up path to each replicate model run}
path10<-"D:/Results_4Populations/gr_Columbia2017B_NoCWR_acute20/gr_Columbia2017B_NoCWR_acute20-[1]/Data Probe/"
path11<-"D:/Results_4Populations/gr_Columbia2017B_NoCWR_acute20/gr_Columbia2017B_NoCWR_acute20-[2]/Data Probe/"
path12<-"D:/Results_4Populations/gr_Columbia2017B_NoCWR_acute20/gr_Columbia2017B_NoCWR_acute20-[3]/Data Probe/"

```

For each replicate imports all CSVs in Data Probe folder into a list of tibbles. Each path defined above needs to be specified below to read in CSVs and create new unique ID.
```{r gr_Columbia2017B_NoCWR_acute20 create unique ID for each CSV for replicates}
## creates a list of tibbles of all CSVs in directory
files1 <- list.files(path = path10, pattern = '.csv$', full.names = T) %>%
  map(read_csv)
#adds a new ID column with original ID and replicate concatenated
for (e in 1:length(files1)){
   files1[[e]]$test1<-rep(1, length(files1[[e]]$ID))
   files1[[e]]$test<-paste(files1[[e]]$ID,files1[[e]]$test1, sep="_")
  }

##
files2 <- list.files(path = path11, pattern = '.csv$', full.names = T) %>%
  map(read_csv)
# adds a new ID column with original ID and replicate concatenated
for (e in 1:length(files2)){
  files2[[e]]$test1<-rep(2, length(files2[[e]]$ID))
  files2[[e]]$test<-paste(files2[[e]]$ID,files2[[e]]$test1, sep="_")
}

##
files3 <- list.files(path = path12, pattern = '.csv$', full.names = T) %>%
  map(read_csv)
# adds a new ID column with original ID and replicate concatenated
for (e in 1:length(files3)){
  files3[[e]]$test1<-rep(3, length(files3[[e]]$ID))
  files3[[e]]$test<-paste(files3[[e]]$ID,files3[[e]]$test1, sep="_")
}

```

Need to specify lists to be combined below (files1, files2, files3). Drops intermediate columns used to create unique ID and re-orders columns to match original order of columns.
```{r gr_Columbia2017B_NoCWR_acute20 combine like replicate DFs from lists into individual DFs}
#### combine tibbles from different lists into DF ####
dir.create("D:/Results_4Populations/gr_Columbia2017B_NoCWR_acute20/combined/")
setwd("D:/Results_4Populations/gr_Columbia2017B_NoCWR_acute20/combined/")

for (f in 1:length(files1)){
  nam <- paste("H", f, sep = "")
  outDF<-rbind(files1[[f]], files2[[f]],  files3[[f]]) # combine tibbles from different lists into DF
  outDF2<-select(outDF, -test1, -ID) # drop intermediate columns
  outDF2<-dplyr::rename(outDF2, ID=test) # rename new ID column
  outDF2<-select(outDF2, Run, Step, Population, ID, everything()) # put new ID column in same location as old
  assign(nam, outDF2) # name DF based on order in CSV list
  fwrite(outDF2, file=paste0(nam, ".csv"),   sep = ",")
  }
```
