---
title: "Grande Ronde summer steelhead 2017B"
author: "MNSnyder"
date: "9/4/2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE)
library(readr)
library(tidyverse)
library(reshape2)
library(ggplot2)
library(knitr)
library(lubridate)
library(plyr)
library(data.table)
```


## Grande Ronde summer steelhead combine replicates. 
Combines replicate output for 4 scenarios- 
* Columbia 2017
* Columbia 2017, no CWRs
* Columbia 2017 + 1 degree
* Columbia 2017 + 1 degree, no CWRs


Combines Data Probe model outputs for replicate model runs into one DF. Unique ID values are created by concatenating ID value with replicate number. 

Need to specify path to individual replicate for a HexSim model run. 

## Columbia 2040 No CWR
```{r Columbia 2017 Current CWR set up path to each replicate model run}
path1<-"D:/Results_4Populations/gr_Columbia2017B/gr_Columbia2017B-[1]/Data Probe/"
path2<-"D:/Results_4Populations/gr_Columbia2017B/gr_Columbia2017B-[2]/Data Probe/"
path3<-"D:/Results_4Populations/gr_Columbia2017B/gr_Columbia2017B-[3]/Data Probe/"

```

For each replicate imports all CSVs in Data Probe folder into a list of tibbles. Each path defined above needs to be specified below to read in CSVs and create new unique ID.
```{r Columbia 2017 Current CWR create unique ID for each CSV for replicates}
## creates a list of tibbles of all CSVs in directory
files1 <- list.files(path = path1, pattern = '.csv$', full.names = T) %>%
  map(read_csv)
#adds a new ID column with original ID and replicate concatenated
for (e in 1:length(files1)){
   files1[[e]]$test1<-rep(1, length(files1[[e]]$ID))
   files1[[e]]$test<-paste(files1[[e]]$ID,files1[[e]]$test1, sep="_")
  }

##
files2 <- list.files(path = path2, pattern = '.csv$', full.names = T) %>%
  map(read_csv)
# adds a new ID column with original ID and replicate concatenated
for (e in 1:length(files2)){
  files2[[e]]$test1<-rep(2, length(files2[[e]]$ID))
  files2[[e]]$test<-paste(files2[[e]]$ID,files2[[e]]$test1, sep="_")
}

##
files3 <- list.files(path = path3, pattern = '.csv$', full.names = T) %>%
  map(read_csv)
# adds a new ID column with original ID and replicate concatenated
for (e in 1:length(files3)){
  files3[[e]]$test1<-rep(3, length(files3[[e]]$ID))
  files3[[e]]$test<-paste(files3[[e]]$ID,files3[[e]]$test1, sep="_")
}

```

Need to specify lists to be combined below (files1, files2, files3). Drops intermediate columns used to create unique ID and re-orders columns to match original order of columns.
```{r Columbia 2017 Current CWR combine like replicate DFs from lists into individual DFs}
#### combine tibbles from different lists into DF ####
# creates DF A1 through A17
# create combined folder before running
dir.create("D:/Results_4Populations/gr_Columbia2017B/combined/")
setwd("D:/Results_4Populations/gr_Columbia2017B/combined/")

for (f in 1:length(files1)){
  nam <- paste("E", f, sep = "")
  outDF<-rbind(files1[[f]], files2[[f]],  files3[[f]]) # combine tibbles from different lists into DF
  outDF2<-select(outDF, -test1, -ID) # drop intermediate columns
  outDF2<-dplyr::rename(outDF2, ID=test) # rename new ID column
  outDF2<-select(outDF2, Run, Step, Population, ID, everything()) # put new ID column in same location as old
  assign(nam, outDF2) # name DF based on order in CSV list
  fwrite(outDF2, file=paste0(nam, ".csv"),   sep = ",")
  }
```

## Columbia 2017 No CWR
```{r Columbia 2017 No CWR Current set up path to each replicate model run}
path4<-"D:/Results_4Populations/gr_Columbia2017B_NoCWR/gr_Columbia2017B_NoCWR-[1]/Data Probe/"
path5<-"D:/Results_4Populations/gr_Columbia2017B_NoCWR/gr_Columbia2017B_NoCWR-[2]/Data Probe/"
path6<-"D:/Results_4Populations/gr_Columbia2017B_NoCWR/gr_Columbia2017B_NoCWR-[3]/Data Probe/"

```

For each replicate imports all CSVs in Data Probe folder into a list of tibbles. Each path defined above needs to be specified below to read in CSVs and create new unique ID.
```{r Columbia 2017 No CWR Current create unique ID for each CSV for replicates}
## creates a list of tibbles of all CSVs in directory
files1 <- list.files(path = path4, pattern = '.csv$', full.names = T) %>%
  map(read_csv)
#adds a new ID column with original ID and replicate concatenated
for (e in 1:length(files1)){
   files1[[e]]$test1<-rep(1, length(files1[[e]]$ID))
   files1[[e]]$test<-paste(files1[[e]]$ID,files1[[e]]$test1, sep="_")
  }

##
files2 <- list.files(path = path5, pattern = '.csv$', full.names = T) %>%
  map(read_csv)
# adds a new ID column with original ID and replicate concatenated
for (e in 1:length(files2)){
  files2[[e]]$test1<-rep(2, length(files2[[e]]$ID))
  files2[[e]]$test<-paste(files2[[e]]$ID,files2[[e]]$test1, sep="_")
}

##
files3 <- list.files(path = path6, pattern = '.csv$', full.names = T) %>%
  map(read_csv)
# adds a new ID column with original ID and replicate concatenated
for (e in 1:length(files3)){
  files3[[e]]$test1<-rep(3, length(files3[[e]]$ID))
  files3[[e]]$test<-paste(files3[[e]]$ID,files3[[e]]$test1, sep="_")
}

```

Need to specify lists to be combined below (files1, files2, files3). Drops intermediate columns used to create unique ID and re-orders columns to match original order of columns.
```{r Columbia 2017 No CWR Current combine like replicate DFs from lists into individual DFs}
#### combine tibbles from different lists into DF ####
dir.create("D:/Results_4Populations/gr_Columbia2017B_NoCWR/combined/")
setwd("D:/Results_4Populations/gr_Columbia2017B_NoCWR/combined/")

for (f in 1:length(files1)){
  nam <- paste("F", f, sep = "")
  outDF<-rbind(files1[[f]], files2[[f]],  files3[[f]]) # combine tibbles from different lists into DF
  outDF2<-select(outDF, -test1, -ID) # drop intermediate columns
  outDF2<-dplyr::rename(outDF2, ID=test) # rename new ID column
  outDF2<-select(outDF2, Run, Step, Population, ID, everything()) # put new ID column in same location as old
  assign(nam, outDF2) # name DF based on order in CSV list
  fwrite(outDF2, file=paste0(nam, ".csv"),   sep = ",")
  }
```

## Columbia 2017 plus 1
```{r Columbia 2017 plus 1 set up path to each replicate model run}
path7<-"D:/Results_4Populations/gr_Columbia2017BplusOne/gr_Columbia2017BplusOne-[1]/Data Probe/"
path8<-"D:/Results_4Populations/gr_Columbia2017BplusOne/gr_Columbia2017BplusOne-[2]/Data Probe/"
path9<-"D:/Results_4Populations/gr_Columbia2017BplusOne/gr_Columbia2017BplusOne-[3]/Data Probe/"

```

For each replicate imports all CSVs in Data Probe folder into a list of tibbles. Each path defined above needs to be specified below to read in CSVs and create new unique ID.
```{r Columbia 2017 plus 1 create unique ID for each CSV for replicates}
## creates a list of tibbles of all CSVs in directory
files1 <- list.files(path = path7, pattern = '.csv$', full.names = T) %>%
  map(read_csv)
#adds a new ID column with original ID and replicate concatenated
for (e in 1:length(files1)){
   files1[[e]]$test1<-rep(1, length(files1[[e]]$ID))
   files1[[e]]$test<-paste(files1[[e]]$ID,files1[[e]]$test1, sep="_")
  }

##
files2 <- list.files(path = path8, pattern = '.csv$', full.names = T) %>%
  map(read_csv)
# adds a new ID column with original ID and replicate concatenated
for (e in 1:length(files2)){
  files2[[e]]$test1<-rep(2, length(files2[[e]]$ID))
  files2[[e]]$test<-paste(files2[[e]]$ID,files2[[e]]$test1, sep="_")
}

##
files3 <- list.files(path = path9, pattern = '.csv$', full.names = T) %>%
  map(read_csv)
# adds a new ID column with original ID and replicate concatenated
for (e in 1:length(files3)){
  files3[[e]]$test1<-rep(3, length(files3[[e]]$ID))
  files3[[e]]$test<-paste(files3[[e]]$ID,files3[[e]]$test1, sep="_")
}

```

Need to specify lists to be combined below (files1, files2, files3). Drops intermediate columns used to create unique ID and re-orders columns to match original order of columns.
```{r Columbia 2017 plus 1 combine like replicate DFs from lists into individual DFs}
#### combine tibbles from different lists into DF ####
dir.create("D:/Results_4Populations/gr_Columbia2017BplusOne/combined/")
setwd("D:/Results_4Populations/gr_Columbia2017BplusOne/combined/")

for (f in 1:length(files1)){
  nam <- paste("G", f, sep = "")
  outDF<-rbind(files1[[f]], files2[[f]],  files3[[f]]) # combine tibbles from different lists into DF
  outDF2<-select(outDF, -test1, -ID) # drop intermediate columns
  outDF2<-dplyr::rename(outDF2, ID=test) # rename new ID column
  outDF2<-select(outDF2, Run, Step, Population, ID, everything()) # put new ID column in same location as old
  assign(nam, outDF2) # name DF based on order in CSV list
  fwrite(outDF2, file=paste0(nam, ".csv"),   sep = ",")
  }
```

## Columbia 2017 plus 1 no CWR
```{r Columbia 2017 plus 1 no CWR set up path to each replicate model run}
path10<-"D:/Results_4Populations/gr_Columbia2017BplusOne_NoCWR/gr_Columbia2017BplusOne_NoCWR-[1]/Data Probe/"
path11<-"D:/Results_4Populations/gr_Columbia2017BplusOne_NoCWR/gr_Columbia2017BplusOne_NoCWR-[2]/Data Probe/"
path12<-"D:/Results_4Populations/gr_Columbia2017BplusOne_NoCWR/gr_Columbia2017BplusOne_NoCWR-[3]/Data Probe/"

```

For each replicate imports all CSVs in Data Probe folder into a list of tibbles. Each path defined above needs to be specified below to read in CSVs and create new unique ID.
```{r Columbia 2017 plus 1 no CWR create unique ID for each CSV for replicates}
## creates a list of tibbles of all CSVs in directory
files1 <- list.files(path = path10, pattern = '.csv$', full.names = T) %>%
  map(read_csv)
#adds a new ID column with original ID and replicate concatenated
for (e in 1:length(files1)){
   files1[[e]]$test1<-rep(1, length(files1[[e]]$ID))
   files1[[e]]$test<-paste(files1[[e]]$ID,files1[[e]]$test1, sep="_")
  }

##
files2 <- list.files(path = path11, pattern = '.csv$', full.names = T) %>%
  map(read_csv)
# adds a new ID column with original ID and replicate concatenated
for (e in 1:length(files2)){
  files2[[e]]$test1<-rep(2, length(files2[[e]]$ID))
  files2[[e]]$test<-paste(files2[[e]]$ID,files2[[e]]$test1, sep="_")
}

##
files3 <- list.files(path = path12, pattern = '.csv$', full.names = T) %>%
  map(read_csv)
# adds a new ID column with original ID and replicate concatenated
for (e in 1:length(files3)){
  files3[[e]]$test1<-rep(3, length(files3[[e]]$ID))
  files3[[e]]$test<-paste(files3[[e]]$ID,files3[[e]]$test1, sep="_")
}

```

Need to specify lists to be combined below (files1, files2, files3). Drops intermediate columns used to create unique ID and re-orders columns to match original order of columns.
```{r Columbia 2017 plus 1 no CWR combine like replicate DFs from lists into individual DFs}
#### combine tibbles from different lists into DF ####
dir.create("D:/Results_4Populations/gr_Columbia2017BplusOne_NoCWR/combined/")
setwd("D:/Results_4Populations/gr_Columbia2017BplusOne_NoCWR/combined/")

for (f in 1:length(files1)){
  nam <- paste("H", f, sep = "")
  outDF<-rbind(files1[[f]], files2[[f]],  files3[[f]]) # combine tibbles from different lists into DF
  outDF2<-select(outDF, -test1, -ID) # drop intermediate columns
  outDF2<-dplyr::rename(outDF2, ID=test) # rename new ID column
  outDF2<-select(outDF2, Run, Step, Population, ID, everything()) # put new ID column in same location as old
  assign(nam, outDF2) # name DF based on order in CSV list
  fwrite(outDF2, file=paste0(nam, ".csv"),   sep = ",")
  }
```
